### 2019-09-29 paper/v1.tex
m

\documentclass[prd,amsmath,amssymb,floatfix,superscriptaddress,nofootinbib,twocolumn]{revtex4-1}

\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\newcommand{\vs}{\nonumber\\}
\newcommand{\vk}{\vec{k}}
\newcommand{\ec}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\eec}[2]{Eqs.~(\ref{eq:#1}) and (\ref{eq:#2})}
\newcommand{\Ec}[1]{(\ref{eq:#1})}
\newcommand{\eql}[1]{\label{eq:#1}}
\newcommand{\sfig}[2]{
\includegraphics[width=#2]{../plots/#1}
        }
\newcommand{\sfigr}[2]{
\includegraphics[angle=270,origin=c,width=#2]{#1}
        }
\newcommand{\sfigra}[2]{
\includegraphics[angle=90,origin=c,width=#2]{#1}
        }
\newcommand{\Sfig}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfig{#1.pdf}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}
\newcommand{\Spng}[2]{
   \begin{figure}[thbp]
   \begin{center}
    \sfig{#1.png}{\columnwidth}
    \caption{{\small #2}}
    \label{fig:#1}
     \end{center}
   \end{figure}
}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{simplewick}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{enumitem}
\usepackage[linktocpage=true]{hyperref} 
\hypersetup{
    colorlinks=true,       
    linkcolor=red,         
    citecolor=blue,        
    filecolor=magenta,      
    urlcolor=blue           
}
\usepackage[all]{hypcap} 
\definecolor{darkgreen}{cmyk}{0.85,0.1,1.00,0} 
\newcommand{\scott}[1]{{\color{darkgreen} #1}}
\newcommand{\peikai}[1]{{\color{blue} #1}}
\newcommand{\WH}[1]{{\color{red} #1}}
\newcommand{\wh}[1]{{\color{red} #1}}
\newcommand{\prvs}[1]{{\color{magenta} #1}}
\newcommand{\AL}[1]{{\color{magenta} AL: #1}}
\newcommand{\MR}[1]{{\color{blue} MR: #1}}
\newcommand{\nl}{\\ \indent}
\begin{document}
\title{Large Scale Modes Reconstruction with Short-Wavelength Modes}
\author{\large Peikai Li}
\author{\large Scott Dodelson}
\author{\large XXX}
\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, Pennsylvania 15312, USA}

\date{\today}
\begin{abstract}

\end{abstract}
\maketitle
\section{Introduction}
\cite{Hu:2002mr}

\section{Standard Perturbation Theory}
In this section we review the SPT\footnote{SPT stands for standard perturbation theory.} approach of describing small scale nonlinearity. In the case of a perfect pressurelesee fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:
\bea
\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\times [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0 \\
(\frac{\partial}{\partial \tau} +\vec{v}(\vec{x},\tau)&\times&\vec{\nabla})\vec{v}(\vec{x},\tau)=-\frac{da}{d\tau}\frac{\vec{v}(\vec{x},\tau)}{a}-\vec{\nabla}\Phi \eql{eulereq}\\
&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) 
\eea
these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$. Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get:
\bea 
\frac{\partial{\delta}}{\partial\tau} + {\theta} &=& -\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12}) \vs
&& \times\frac{\vk \cdot \vk_1}{k_1^2}{\theta}(\vk_1,\tau){\delta}(\vk_2,\tau) \eql{fouriercont}\\
\frac{\partial{\delta}}{\partial\tau}+\frac{da}{d\tau}\frac{{\theta}}{a}+\frac{6}{\tau^2}{\delta}&=&-\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12})\vs
&&\times \frac{k^2(\vk_1 \cdot \vk_2)}{2k_1^2 k_2^2} {\theta}(\vk_1,\tau){\theta}(\vk_2,\tau) \eql{fouriereuler}
\eea
here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion \cite:
\bea
{\delta}(\vk,\tau)&=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}a^{n}(\tau)\delta_{n}(\vk) \\ {\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)=-H(\tau)\sum_{n=1}^{\infty}a^{n+1}(\tau)\theta_{n}(\vk) 
\eea
\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution. Linear power spectrum is given by this term via:
\be 
\langle {\delta}(\vk){\delta}(\vk') \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k) \eql{lin}
\ee 
Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ \cite{cite} with solution:
\bea
{\delta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
&&\times F_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n}) \\
{\theta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
&&\times G_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n})
\eea
and recursion relations are encoded in kernels $F_n$ and $G_n$. Since we only consider up to second-order, the second-order symmetrized kernels are given by:
\bea 
F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}) \\
G_{2}(\vk_1,\vk_2)=\frac{3}{7}+\frac{4}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})
\eea 
This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{123} with a slight generalization:
\bea
{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk) \\
{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)\vs
&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) 
\eea
Time-dependent second-order density contrast can be expressed as convolution of two linear density fields with kernel $F_2$:
\be 
{\delta}^{(2)}(\vk,\tau)=\int \frac{d^{3}\vk_{1}}{(2\pi)^3} F_2(\vk_1,\vk-\vk_1){\delta}^{(1)}(\vk_1,\tau) {\delta}^{(1)}(\vk-\vk_1,\tau) \eql{sorder}
\ee 
\\Discussion (Accuracy?...)

\section{Quadratic Estimator}
Comparison with CMB lensing \cite{123} \\
Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $|\vk_s+\vk_s'|\ll |\vk_s|, \,|\vk_s'|$ up two second-order ($\tau$ is fixed):
\bea 
&& \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{(\vk_s+\vk_s')\neq 0}
\vs 
&=&  \langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(2)}(\vec{k}_s') \rangle+\langle {\delta}^{(2)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s') \rangle
\eea 
Substituting \ec{sorder} into the first bracket we get:
\bea 
\langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(2)}(\vec{k}_s') \rangle =  \int \frac{d^3\vec{k}}{(2\pi)^3} F_2 (\vec{k},\vec{k}_s'-\vec{k})\vs
\times \langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s'-\vec{k}){\delta}^{(1)}(\vec{k}) \rangle \eql{integral}
\eea 
This correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
\be 
\langle
\contraction{}{{\delta}}{{\delta}(\vk_s'\,}{}
{\delta}(\vk_s) {\delta}(\vk_s'){\delta}(\vk_l) 
\rangle
=\langle {\delta}(\vk_s) {\delta}(\vk_s') \rangle {\delta}(\vk_l) 
\ee 
Since in a real life survey, we can only measure this long-wavelength mode once. Thus it won't have any statistical property and we can safely extract this term out of the bracket.\\
We can do this contraction twice in this integral. One occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, we can extract ${\delta}^{(1)}(\vk)$ out; the other one occurs when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\
Use \ec{lin} the integral in \ec{integral} can be evaluated as:
\bea 
&&\int \frac{d^3\vec{k}}{(2\pi)^3} F_2 (\vec{k},\vec{k}_s'-\vec{k})\langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s'-\vec{k}){\delta}^{(1)}(\vec{k}) \rangle \vs
&=&\int d^3\vk F_2(\vec{k},\vec{k}_s'-\vec{k}) \delta_{\rm D}(\vk_s+\vk_s'-\vk)P_{\rm 
lin}(k_s){\delta}^{(1)}(\vec{k}) \vs
&+&\int d^3\vk F_2(\vec{k},\vec{k}_s'-\vec{k}) \delta_{\rm D}(\vk_s+\vk)P_{\rm 
lin}(k_s){\delta}^{(1)}(\vk_s'-\vk) \vs
&=&2F_2(-\vk_s,\vk_s+\vk_s')P_{\rm lin}(k_s){\delta}^{(1)}(\vk_s+\vk_s')
\eea 
Finally we have:
\be 
\langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle =f(\vec{k}_s,\vec{k}_s'){\delta}^{(1)}(\vec{k}_s+\vk_s') \eql{2pt}
\ee 
with
\bea
f(\vec{k}_s,\vec{k}_s')&=&2F_2(-\vec{k}_s,\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s)\vs
&+&2F_2(-\vec{k}_s',\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s')       
\eea 
\ec{2pt} suggests that we can estimate long-wavelength modes with appropriate average over pairs of shart-wavelength modes. General form of the quadratic estimator can be written as:
\begin{eqnarray}
\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s')
\end{eqnarray} 
with $g$ being weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ is defined via $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
\begin{eqnarray}
A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1}
\end{eqnarray}
The Gaussian noise is given by:
\be 
\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}[\vk_{l}-\vk_{l}')(P_{\rm lin}(k_{l})+N(\vk_l)]
\ee 
with 
\begin{eqnarray}
&&N(\vec{k}_{l})=2A^2(k_{l})\vs
&&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
\end{eqnarray}
where $P_{\rm nl}$ is the nonlinear power spectrum. Minimizing the noise term we can fix the form of $g$ to be:
\begin{eqnarray}
g(\vec{k}_{s},\vec{k}_{s}')=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}
\end{eqnarray} 
Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.
\section{Discussion}

\acknowledgements
We thank XXX for resourceful discussions.  SD and PL were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
%\input{main.bbl}
\bibliography{refs}
\end{document}

### 2019-09-29 source/N.py

@@ -1,75 +1,0 @@
-import matplotlib.pyplot as plt
-import scipy.integrate as integrate
-import scipy.special as special
-from scipy import interpolate
-from sympy.physics.wigner import wigner_3j
-import numpy as np
-from scipy import interpolate
-
-filename = ''
-font = {#'family' : 'normal',
-                #'weight' : 'bold',
-                'size'  : 18}
-
-plt.rc('font', **font)
-#############################################################################################################################################################################################################
-### DATA from Cosmosis, DEMO1. I didn't change any of the input values (h=0.6726, omega_m=0.3141, omega_b=0.04, omega_k=0. yhe=0.245341, tau=0.08, n_s=0.96, A_s=2.1e-9, k_s=0.05, w=-1.0.) #################
-#############################################################################################################################################################################################################
-
-h=0.6726
-
-k = np.loadtxt('data/k.txt')
-pk = np.loadtxt('data/pk.txt')
-#############################################################################################################################################################################################################
-### pk is the linear power spectrum in Mpc3, k wavevector in Mpc-1; Hubble constant h has been obsorbed. ####################################################################################################
-#############################################################################################################################################################################################################
-
-matter_power_lin = interpolate.interp1d(k, pk)
-
-def F_2(ks,cos_theta,kl): # F_2(-ks,ks+ks') in text
-	return (5+2*cos_theta*cos_theta)/7-0.5*cos_theta*(ks/kl+kl/ks)
-
-def norm_ks_prime(ks,cos_theta,kl): # |ks'|=|ks-kl|
-	return np.sqrt(ks*ks-2*ks*kl*cos_theta+kl*kl)
-
[…]

### 2019-09-29 source/int1.cc

@@ -280,7 +280,7 @@ main(int argc, char* argv[])
 
   std::cout << "Finished Reading xk" << "\n";
 
-  std::ifstream file5("../Example/data/k_h.txt");
+  std::ifstream file5("../Example/data/k_h_lin.txt");
   std::vector<double> k_h;
 
   while(!file5.eof())
@@ -291,7 +291,7 @@ main(int argc, char* argv[])
 
   std::cout << "Finished Reading kh" << "\n";
 
-  std::ifstream file6("../Example/data/p_h.txt");
+  std::ifstream file6("../Example/data/p_h_lin.txt");
   std::vector<double> p_h;
 
   while(!file6.eof())
@@ -344,32 +344,32 @@ main(int argc, char* argv[])
 
   // for(N_ks_x=92;N_ks_x<=200;N_ks_x=N_ks_x+12){
   //     for(N_ks_y=92;N_ks_y<=200;N_ks_y=N_ks_y+12){
-  //     	for(N_ks_z=-92;N_ks_z>=-200;N_ks_z=N_ks_z-12){
-  //     		Int = 0.;
-  //     		sum_index = 0;
+  //      for(N_ks_z=-92;N_ks_z>=-200;N_ks_z=N_ks_z-12){
+  //        Int = 0.;
+  //        sum_index = 0;
 
   //         for(N_kl_x=-upper_int;N_kl_x<=upper_int;N_kl_x=N_kl_x+2){
-  //     		  for(N_kl_y=-upper_int;N_kl_y<=upper_int;N_kl_y=N_kl_y+2){
-  //     		    for(N_kl_z=-upper_int;N_kl_z<=upper_int;N_kl_z=N_kl_z+2){
-  //     		    	if(((N_kl_x*N_kl_x+N_kl_y*N_kl_y+N_kl_z*N_kl_z)<=upper_int*upper_int)&&((N_kl_x*N_kl_x+N_kl_y*N_kl_y+N_kl_z*N_kl_z)!=0)&&(((N_ks_x-N_kl_x)*(N_ks_x-N_kl_x)+(N_ks_y-N_kl_y)*(N_ks_y-N_kl_y)+(N_ks_z-N_kl_z)*(N_ks_z-N_kl_z))!=0)){
-  //     		    	  sum_index = sum_index+1;
-  //           	    M_kl = std::sqrt(N_kl_x*N_kl_x+N_kl_y*N_kl_y+N_kl_z*N_kl_z);
[…]

### 2019-10-02 paper/v1.tex
1

@@
 \begin{document}
-\title{Large Scale Modes Reconstruction with Short-Wavelength Modes}
+\title{Large Scale Density Reconstruction with Short-Wavelength Modes}
 \author{\large Peikai Li}
@@
 \begin{abstract}
-
+We can learn about the universe on large scales by measuring perturbations on small scales. 
 \end{abstract}
@@
 these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
-Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get:
+Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get time evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$:
 \bea 
@@
 Comparison with CMB lensing \cite{123} \\
-Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $|\vk_s+\vk_s'|\ll |\vk_s|, \,|\vk_s'|$ up two second-order ($\tau$ is fixed):
+Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $|\vk_s+\vk_s'|\ll |\vk_s|, \,|\vk_s'|$ up to second-order ($\tau$ is fixed):
 \bea 
@@
 \eea 
-This correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
+We claim that this correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
 \be 
@@
 \begin{eqnarray}
-&&N(\vec{k}_{l})=2A^2(k_{l})\vs
+&&N(\vec{k}_{l})=2A^2(\vk_{l})\vs
 &&\times\int \frac{d^3 \vec{k}_{s}}{(2\pi)^3} g^2(\vec{k}_{s},\vk_l-\vec{k}_{s})P_{\rm nl}(k_{s})P_{\rm nl}(|\vk_l-\vk_s|)
@@
 \end{eqnarray} 
-Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.
+Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.\\
+Plot of $P$ vs. $A$ on large scales.
+
+\section{N-Body Simulation}
+We tested the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations\cite{Klypin:2014nov}.
+
 \section{Discussion}
@@
 \acknowledgements
-We thank XXX for resourceful discussions.  SD and PL were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
+We thank Lam Hui, XXX for resourceful discussions.  SD and PL were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
 %\input{main.bbl}

### 2019-10-06 paper/v1.tex
paper

--- 2019-09-29 paper/v1.tex
@@
 \newcommand{\eql}[1]{\label{eq:#1}}
+\newcommand{\rf}[1]{\ref{fig:#1}}
 \newcommand{\sfig}[2]{
 \includegraphics[width=#2]{../plots/#1}
+        }
+\newcommand{\sfigg}[2]{
+\includegraphics[width=0.45\paperwidth]{../plots/#1}
         }
@@
    \begin{center}
-    \sfig{#1.pdf}{\columnwidth}
+    \sfig{../plots/#1.pdf}{\columnwidth}
     \caption{{\small #2}}
@@
 }
+\newcommand{\Sfigg}[2]{
+   \begin{figure}[thbp]
+    \sfigg{../plots/#1.pdf}{\columnwidth}
+    \caption{{\small #2}}
+    \label{fig:#1}
+   \end{figure}
+}
 \newcommand{\Spng}[2]{
@@
    \begin{center}
-    \sfig{#1.png}{\columnwidth}
+    \sfigg{../plots/#1.png}{\columnwidth}
     \caption{{\small #2}}
@@
 \begin{document}
-\title{Large Scale Modes Reconstruction with Short-Wavelength Modes}
+\title{Large Scale Structure Reconstruction with Short-Wavelength Modes}
 \author{\large Peikai Li}
+\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
 \author{\large Scott Dodelson}
-\author{\large XXX}
-\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, Pennsylvania 15312, USA}
+\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+\author{\large Rupert A. C. Croft}
+\affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
 
@@
 \begin{abstract}
+\noindent Large scale density modes cannot be measured directly through surveys but we can study them by measuring perturbations on small scales.
+Cosmological perturbation theory predicts that second-order density inhomogeneities can be considered as convolution of a short- and long-wavelength mode.
+This arises physically because small structure structure varies depending on the large scale environment in which it resides.
+And this will induce an off-diagonal term of two-point density correlations, from which we can build a quadratic estimator with the same form as CMB lensing estimator.
+We tested the robustness of the theory using data from large cosmological N-body simulation.
+We checked the accuracy of large scale density modes from this quadratic estimator and discussed signal-to-noise and potential bias of the theory.
 
@@
 \section{Introduction}
-\cite{Hu:2002mr}
+Measuring large scale structures of order $10^3\, \rm Mpc$ has been one of the main goals of recent surveys despite it is extremely difficult to get a direct detection.
+To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
+Method of using small scale position-dependent power spectrum to compute squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
+In order to fully accomplish this goal, we develop in this work a generalized approach of building a quadratic estimator for long-wavelength modes.
+\\
+Starting from second-order SPT\footnote{SPT stands for standard perturbation theory.} \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify the second-order correction of a short-wavelength mode as a convolution of a short- and long-wavelength mode.
+This can be further related to CMB lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight.
+Similarly in this case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
+\\
+Inspired by CMB lensing quadratic estimator's construction, where small scale temperature correlation functions have off-diagonal terms due to
+large scale perturbations caused by gravitational lensing.
+The same procedure applies in our case as well - off-diagonal terms of small scale correlations are no-longer zero due to large scale modes.
+Thus we can create quadratic estimator for long-wavelength modes using exact same routine.
+\\
+We begin with a brief review of standard perturbation theory and its detailed formalism up to second-order in section \ref{sec1}.
+Then we build the quadratic estimator and compute signal-to-noise of the estimator in section \ref{sec2}.
+In \ref{sec3} we present a concise study of the estimator with data from N-body simulation.
+Finally we discuss applications of the estimator and future work related to this in section \ref{sec4}.
+We use $\Lambda$CDM universe with the Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
 
-\section{Standard Perturbation Theory}
-In this section we review the SPT\footnote{SPT stands for standard perturbation theory.} approach of describing small scale nonlinearity.
+\section{Standard Perturbation Theory}\label{sec1}
+In this section we review the SPT approach of describing small scale nonlinearity.
 In the case of a perfect pressurelesee fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:
@@
 \ee 
-Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ \cite{cite} with solution:
+Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ with solution:
 \bea
@@
 \eea 
-This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{123} with a slight generalization:
+This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with a slight generalization:
 \bea
@@
 \ee 
-\\Discussion (Accuracy?...)
+Second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.
 
-\section{Quadratic Estimator}
+\section{Quadratic Estimator}\label{sec2}
 Comparison with CMB lensing \cite{123} \\
-Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $|\vk_s+\vk_s'|\ll |\vk_s|, \,|\vk_s'|$ up two second-order ($\tau$ is fixed):
+Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $|\vk_s+\vk_s'|\ll |\vk_s|, \,|\vk_s'|$ up to second-order ($\tau$ is fixed):
 \bea 
@@
 \eea 
-This correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
+We claim that this correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
 \be 
 \langle
-\contraction{}{{\delta}}{{\delta}(\vk_s'\,}{}
-{\delta}(\vk_s) {\delta}(\vk_s'){\delta}(\vk_l) 
+\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
+{\delta^{(1)}}(\vk_s) {\delta^{(1)}}(\vk_s'){\delta^{(1)}}(\vk_l) 
 \rangle
-=\langle {\delta}(\vk_s) {\delta}(\vk_s') \rangle {\delta}(\vk_l) 
+=\langle {\delta^{(1)}}(\vk_s) {\delta^{(1)}}(\vk_s') \rangle {\delta^{(1)}}(\vk_l) 
 \ee 
-Since in a real life survey, we can only measure this long-wavelength mode once. Thus it won't have any statistical property and we can safely extract this term out of the bracket.\\
+Since in a real life survey, we can only measure this long-wavelength mode limited times.
+Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.\\
 We can do this contraction twice in this integral.
@@
 \begin{eqnarray}
-\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s')
+\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest}
 \end{eqnarray} 
@@
 \end{eqnarray} 
-Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.
-\section{Discussion}
+Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.\\
+\Sfig{SN}{Detectability of long-wavelength modes. We use a toy survey of boxsize $6\, h\rm Mpc^{-1}$.}
+
+\section{N-Body Simulation}\label{sec3}
+We test the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
+Boxsize of BigMDPL is $2.5\, h\rm Mpc^{-1}$, where $h=0.6777$.
+\\
+We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ in Fig.~\rf{hist}.
+$\delta(\vk_l)$ is the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ is the reproduced modes using quadratic estimator \ec{quadest}.\\
+\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.
+We can see that in the weakly nonlinear regime, left plot peaks at $1$ which is what we would expect.
+While for the right plot, when we go higher into nonlinear scale, ratio peak at about $1.3$.
+This bias comes from the inaccuracy of second-order perturbation theory.}
+
+Ultimate goal of this approach is to reproduce large scale structure in real space.
+Compare $\delta$ and $\hat{\delta}$ in real space in Fig.~\rf{real} and we can see the quadratic estimator is quite effective for this simulation.
+\Sfigg{real}{Comparison between $\delta(\vec{x})$ and $\hat{\delta}(\vec{x})$ and their difference.
+The 3D grids of data points are unfolded into 2D grids.
+The upper limit of $\vk_s$ is chosen to be $0.15 \, \rm Mpc^{-1}$.}
+
+\section{Discussion}\label{sec4}
 
 \acknowledgements
-We thank XXX for resourceful discussions.  SD and PL were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
+\noindent We thank Adam Solomon, Andresa Campos, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.
+SD, PL and RC were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.\\
+The BigMDPL simulation has been performed at LRZ Munich within the PRACE project pr86bu.
+The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
 %\input{main.bbl}

### 2019-10-06 paper/v1.tex
1

@@
 In \ref{sec3} we present a concise study of the estimator with data from N-body simulation.
-Finally we discuss applications of the estimator and future work related to this in section \ref{sec4}.
+Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
 We use $\Lambda$CDM universe with the Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
@@
 here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
-In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion \cite:
+In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion:
 \bea
@@
 \section{Quadratic Estimator}\label{sec2}
-Comparison with CMB lensing \cite{123} \\
-Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $|\vk_s+\vk_s'|\ll |\vk_s|, \,|\vk_s'|$ up to second-order ($\tau$ is fixed):
+Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order ($\tau$ is fixed):
 \bea 
-&& \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{(\vk_s+\vk_s')\neq 0}
+&& \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{\vk_s+\vk_s'=\vk_l}
 \vs 
@@
 \eea 
-We claim that this correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
+We claim that generally correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
 \be 
@@
 \contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
-{\delta^{(1)}}(\vk_s) {\delta^{(1)}}(\vk_s'){\delta^{(1)}}(\vk_l) 
+{\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}'){\delta^{(1)}}(\vk_l') 
 \rangle
-=\langle {\delta^{(1)}}(\vk_s) {\delta^{(1)}}(\vk_s') \rangle {\delta^{(1)}}(\vk_l) 
+=\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}') \rangle {\delta^{(1)}}(\vk_l') 
 \ee 
@@
 \be 
-\langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle =f(\vec{k}_s,\vec{k}_s'){\delta}^{(1)}(\vec{k}_s+\vk_s') \eql{2pt}
+\langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle =f(\vec{k}_s,\vec{k}_s'){\delta}^{(1)}(\vec{k}_l) \eql{2pt}
 \ee 
@@
 Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.\\
-\Sfig{SN}{Detectability of long-wavelength modes. We use a toy survey of boxsize $6\, h\rm Mpc^{-1}$.}
+\Sfig{SN}{Detectability of long-wavelength modes. We use a toy survey of boxsize $8.85\, \rm Gpc$.}
 
@@
 We test the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
-Boxsize of BigMDPL is $2.5\, h\rm Mpc^{-1}$, where $h=0.6777$.
-\\
+Boxsize of BigMDPL is $3.7\,\rm Gpc$.
+We use dark matter particle data to produce matter inhomogeneities.
+Galaxy bias should be considered if we use galaxy catalog.\\
 We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ in Fig.~\rf{hist}.
@@
 
-\section{Discussion}\label{sec4}
+\section{Conclusion}\label{sec4}
+In this paper, we have proposed a new and powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
+The noise term $N=A$ would reduce significantly if we go higher into nonlinear regime while second-order SPT is no longer accurate in this case.
+Thus if we want to detect even larger scales, we might need to use contributions from higher order perturbations and expand the integration range to reduce noise level.
+\\
+Our quadratic estimator of long-wavelength modes in this paper is only valid in a box at a given cosmological time.
+While in real photometric redshift surveys we would deal with light cones instead of boxes.
+Thus we expect the expression for the quadratic estimator to be generalized in that case.
+Also when applied to halos or galaxies, this approach can be used to help determine galaxy bias.
+We leave these to future work.
 
 \acknowledgements
-\noindent We thank Adam Solomon, Andresa Campos, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.
-SD, PL and RC were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.\\
+\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  SD, PL and RC were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.\\
 The BigMDPL simulation has been performed at LRZ Munich within the PRACE project pr86bu.

### 2019-10-07 paper/v1.tex
1

@@
 Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
-We use $\Lambda$CDM universe with the Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
+We use $\Lambda$CDM universe with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
 
 \section{Standard Perturbation Theory}\label{sec1}
-In this section we review the SPT approach of describing small scale nonlinearity.
+In this section we review the SPT approach which describes small scale nonlinearity.
 In the case of a perfect pressurelesee fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:
@@
 these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
-Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get time evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$:
+Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$ in Fourier space:
 \bea 
@@
 \eea
-\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution. Linear power spectrum is given by this term via:
+\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution.
+Linear power spectrum is given by this first order term via:
 \be 
@@
 \eea 
-This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with a slight generalization:
+This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with slight generalization \cite{Bernardeau:2002rev}:
 \bea
@@
 \section{Quadratic Estimator}\label{sec2}
-Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order ($\tau$ is fixed):
+For the remainder if the paper, we use subscript $s$ to represent small scale or short-wavelength modes, while $l$ stands for large scale or long-wavelength modes. We also fix $\tau$ at today.\\
+Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order:
 \bea 
@@
 \contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
-{\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}'){\delta^{(1)}}(\vk_l') 
+{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
 \rangle
-=\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}') \rangle {\delta^{(1)}}(\vk_l') 
+=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3) 
 \ee 
-Since in a real life survey, we can only measure this long-wavelength mode limited times.
+$\vk_1$ and $\vk_2$ corresponds to two arbitrary short modes and $\vk_3$ arbitrary long mode.
+The above equation is true since in a real life survey, we can only measure this long-wavelength mode very limited times.
 Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.\\
@@
 \eea 
-Finally we have:
+where we use the fact that $F_2$ is symmetric function. Finally we have:
 \be 
@@
 \be 
-\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}[\vk_{l}-\vk_{l}')(P_{\rm lin}(k_{l})+N(\vk_l)]
+\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
 \ee 
@@
 Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.\\
-\Sfig{SN}{Detectability of long-wavelength modes. We use a toy survey of boxsize $8.85\, \rm Gpc$.}
+\Sfig{SN}{Detectability of long-wavelength modes. We assume a toy survey of boxsize $8.85\, \rm Gpc$.}
 

### 2019-10-07 paper/v1.tex
1

@@
 \rangle
-=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3) 
+=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction}
 \ee 
@@
 \\
+Another concern is the range of long-wavelength modes we are able to detect.
+In the N-body simulation, we use $k_l$ from largest possible mode $1.7 \times 10^{-3} \, \rm Mpc^{-1}$ to $8.9\times 10^{-3} \, \rm Mpc^{-1}$.
+If we try to measure smaller modes, the quadratic estimator approach would be inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
 Our quadratic estimator of long-wavelength modes in this paper is only valid in a box at a given cosmological time.

### 2019-10-07 paper/v1.tex
1

@@
 Our quadratic estimator of long-wavelength modes in this paper is only valid in a box at a given cosmological time.
-While in real photometric redshift surveys we would deal with light cones instead of boxes.
-Thus we expect the expression for the quadratic estimator to be generalized in that case.
+While in photometric redshift surveys we would deal with light cones instead of boxes.
+Thus we expect the expression for the quadratic estimator to be generalized for photometric surveys.
 Also when applied to halos or galaxies, this approach can be used to help determine galaxy bias.

### 2019-10-07 paper/v1.tex
1

@@
 Thus we expect the expression for the quadratic estimator to be generalized for photometric surveys.
-Also when applied to halos or galaxies, this approach can be used to help determine galaxy bias.
+Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshift, in order to include more nonlinear information.
+When applied to halos or galaxies, this approach can be used to help determine galaxy bias.
 We leave these to future work.

### 2019-10-07 paper/v1.tex
1

@@
 Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
-We use $\Lambda$CDM universe with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
+We use flat $\Lambda$CDM universe model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
 
@@
 \Sfigg{real}{Comparison between $\delta(\vec{x})$ and $\hat{\delta}(\vec{x})$ and their difference.
-The 3D grids of data points are unfolded into 2D grids.
+The 3D grid of data points are unfolded into 2D grids, $7$ columns corresponds to $7$ slices we have.
 The upper limit of $\vk_s$ is chosen to be $0.15 \, \rm Mpc^{-1}$.}

### 2019-10-07 paper/v1.tex
1

@@
 Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
-We use flat $\Lambda$CDM universe model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
+We use flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
 

### 2019-10-08 paper/v1.tex
1

@@
 \newcommand{\sfigg}[2]{
-\includegraphics[width=0.45\paperwidth]{../plots/#1}
+\includegraphics[width=0.9\paperwidth]{../plots/#1}
         }
@@
 \newcommand{\Sfigg}[2]{
-   \begin{figure}[thbp]
+   \begin{figure*}[thbp]
     \sfigg{../plots/#1.pdf}{\columnwidth}
@@
     \label{fig:#1}
-   \end{figure}
+   \end{figure*}
 }
@@
 \noindent Large scale density modes cannot be measured directly through surveys but we can study them by measuring perturbations on small scales.
-Cosmological perturbation theory predicts that second-order density inhomogeneities can be considered as convolution of a short- and long-wavelength mode.
+Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
 This arises physically because small structure structure varies depending on the large scale environment in which it resides.
-And this will induce an off-diagonal term of two-point density correlations, from which we can build a quadratic estimator with the same form as CMB lensing estimator.
-We tested the robustness of the theory using data from large cosmological N-body simulation.
-We checked the accuracy of large scale density modes from this quadratic estimator and discussed signal-to-noise and potential bias of the theory.
+This will induce position-dependent clustering in real space and an off-diagonal term in two-point statistics in Fourier space.
+Therefore we can build a quadratic estimator for the large scale field.
+We demonstrate that this quadratic estimator works amazingly well for our N-body simulation test.
 
@@
 \section{Introduction}
-Measuring large scale structures of order $10^3\, \rm Mpc$ has been one of the main goals of recent surveys despite it is extremely difficult to get a direct detection.
+Measuring the distribution of structures on large scales has been one of the main goals of recent surveys despite it is hard to accomplish directly.
 To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
 Method of using small scale position-dependent power spectrum to compute squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
-In order to fully accomplish this goal, we develop in this work a generalized approach of building a quadratic estimator for long-wavelength modes.
+In order to achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly.
 \\
-Starting from second-order SPT\footnote{SPT stands for standard perturbation theory.} \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify the second-order correction of a short-wavelength mode as a convolution of a short- and long-wavelength mode.
-This can be further related to CMB lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight.
+Starting from second-order standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
+This can be further related to cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight.
 Similarly in this case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
 \\
-Inspired by CMB lensing quadratic estimator's construction, where small scale temperature correlation functions have off-diagonal terms due to
-large scale perturbations caused by gravitational lensing.
+During CMB lensing quadratic estimator's construction, small scale two-point correlation of CMB temperature modes has off-diagonal terms due to large scale perturbations caused by gravitational lensing.
 The same procedure applies in our case as well - off-diagonal terms of small scale correlations are no-longer zero due to large scale modes.
-Thus we can create quadratic estimator for long-wavelength modes using exact same routine.
+Thus we can create a quadratic estimator for long-wavelength modes using the exact same formalism.
 \\
-We begin with a brief review of standard perturbation theory and its detailed formalism up to second-order in section \ref{sec1}.
-Then we build the quadratic estimator and compute signal-to-noise of the estimator in section \ref{sec2}.
-In \ref{sec3} we present a concise study of the estimator with data from N-body simulation.
+We begin with a brief review of SPT up to second-order in section \ref{sec1}.
+Then we build the quadratic estimator and compute the detectability of the estimator in section \ref{sec2}.
+In section \ref{sec3} we present a concise study of the estimator with data from N-body simulation.
 Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
@@
 In this section we review the SPT approach which describes small scale nonlinearity.
-In the case of a perfect pressurelesee fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:
+Then we compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
+This off-diagonal term proportional to \peikai{with or without an "a"?}long-wavelength mode will be the key factor of constructing the quadratic estimator.
+\\
+Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:
 \bea
-\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\times [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0 \\
+\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\times [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0\eql{fluid1} \\
 (\frac{\partial}{\partial \tau} +\vec{v}(\vec{x},\tau)&\times&\vec{\nabla})\vec{v}(\vec{x},\tau)=-\frac{da}{d\tau}\frac{\vec{v}(\vec{x},\tau)}{a}-\vec{\nabla}\Phi \eql{eulereq}\\
-&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) 
+&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) \eql{fluid3}
 \eea
-these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
-Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$ in Fourier space:
+these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.\\
+We can solve these equations in Fourier space with perturbative expansion \cite{Bernardeau:2002rev}:
 \bea
-\frac{\partial{\delta}}{\partial\tau} + {\theta} &=& -\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12}) \vs
-&& \times\frac{\vk \cdot \vk_1}{k_1^2}{\theta}(\vk_1,\tau){\delta}(\vk_2,\tau) \eql{fouriercont}\\
-\frac{\partial{\delta}}{\partial\tau}+\frac{da}{d\tau}\frac{{\theta}}{a}+\frac{6}{\tau^2}{\delta}&=&-\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12})\vs
-&&\times \frac{k^2(\vk_1 \cdot \vk_2)}{2k_1^2 k_2^2} {\theta}(\vk_1,\tau){\theta}(\vk_2,\tau) \eql{fouriereuler}
+{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk)  \eql{pert1}\\
+{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau) \vs
+&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) \eql{pert2}
 \eea
-here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
-In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion:
-\bea
-{\delta}(\vk,\tau)&=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}a^{n}(\tau)\delta_{n}(\vk) \\ {\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)=-H(\tau)\sum_{n=1}^{\infty}a^{n+1}(\tau)\theta_{n}(\vk)
-\eea
-\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution.
-Linear power spectrum is given by this first order term via:
+where $D_1$ is the linear growth factor. The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The inear power spectrum is given by this first order term via:
 \be 
-\langle {\delta}(\vk){\delta}(\vk') \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k) \eql{lin}
+\langle {\delta^{(1)}}(\vk,\tau){\delta^{(1)}}(\vk',\tau) \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k,\tau) \eql{lin}
 \ee 
-Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ with solution:
-\bea
-{\delta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
-&&\times F_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n}) \\
-{\theta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
-&&\times G_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n})
-\eea
-and recursion relations are encoded in kernels $F_n$ and $G_n$. Since we only consider up to second-order, the second-order symmetrized kernels are given by:
-\bea 
-F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}) \\
-G_{2}(\vk_1,\vk_2)=\frac{3}{7}+\frac{4}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})
-\eea 
-This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with slight generalization \cite{Bernardeau:2002rev}:
-\bea
-{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk) \\
-{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)\vs
-&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) 
-\eea
-Time-dependent second-order density contrast can be expressed as convolution of two linear density fields with kernel $F_2$:
+Plugging the perturbative series \ec{pert1} and \ec{pert2} into the fluid equations \ec{fluid1}-\ec{fluid3} after Fourier transform, we can solve second-order density contrast and the result is given by:
 \be
@@
 \ee
-Second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.
-
-\section{Quadratic Estimator}\label{sec2}
-For the remainder if the paper, we use subscript $s$ to represent small scale or short-wavelength modes, while $l$ stands for large scale or long-wavelength modes. We also fix $\tau$ at today.\\
-Compute the correlation function of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order:
+with 
+\be
+F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})\eql{f2}
+\ee
+Notice \ec{f2} is derived in Einstein-de Sitter universe.
+Nonetheless when we actually do relative calculation in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{f2} throughout the whole work.\\
+Compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order where $\vk_l$ corresponds to a long-wavelength mode we have ($\tau$ is fixed at today):
 \bea 
@@
 \eea 
-We claim that generally correlation function with three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
+We claim that generally correlation function of three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
 \be 
@@
 Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.\\
-We can do this contraction twice in this integral.
+We can do this contraction twice in this integral \ec{integral}.
 One occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, we can extract ${\delta}^{(1)}(\vk)$ out; the other one occurs when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\
@@
 \eea 
-\ec{2pt} suggests that we can estimate long-wavelength modes with appropriate average over pairs of shart-wavelength modes. General form of the quadratic estimator can be written as:
+\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.
+Also notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.
+
+%Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$ in Fourier space:
+%\bea 
+%\frac{\partial{\delta}}{\partial\tau} + {\theta} &=& -\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12}) \vs
+%&& \times\frac{\vk \cdot \vk_1}{k_1^2}{\theta}(\vk_1,\tau){\delta}(\vk_2,\tau) \eql{fouriercont}\\
+%\frac{\partial{\delta}}{\partial\tau}+\frac{da}{d\tau}\frac{{\theta}}{a}+\frac{6}{\tau^2}{\delta}&=&-\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12})\vs
+%&&\times \frac{k^2(\vk_1 \cdot \vk_2)}{2k_1^2 k_2^2} {\theta}(\vk_1,\tau){\theta}(\vk_2,\tau) \eql{fouriereuler}
+%\eea
+%here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
+%In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion:
+%\bea
+%{\delta}(\vk,\tau)&=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}a^{n}(\tau)\delta_{n}(\vk) \\ {\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)=-H(\tau)%\sum_{n=1}^{\infty}a^{n+1}(\tau)\theta_{n}(\vk)
+%\eea
+%\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution.
+Linear power spectrum is given by this first order term via:
+%\be 
+%\langle {\delta}(\vk){\delta}(\vk') \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k) \eql{lin}
+%\ee 
+%Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ with solution:
+%\bea
+%{\delta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
+%&&\times F_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n}) \\
+%{\theta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
+%&&\times G_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n})
+%\eea
+%and recursion relations are encoded in kernels $F_n$ and $G_n$. Since we only consider up to second-order, the second-order symmetrized kernels are given by:
+%\bea 
+%F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}) \\
+%G_{2}(\vk_1,\vk_2)=\frac{3}{7}+\frac{4}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})
+%\eea 
+%This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with slight generalization \cite{Bernardeau:2002rev}:
+%\bea
+%{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk) \\
+%{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)\vs
+%&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) 
+%\eea
+%Time-dependent second-order density contrast can be expressed as convolution of two linear density fields with kernel $F_2$:
+%\be 
+%{\delta}^{(2)}(\vk,\tau)=\int \frac{d^{3}\vk_{1}}{(2\pi)^3} F_2(\vk_1,\vk-\vk_1){\delta}^{(1)}(\vk_1,\tau) {\delta}^{(1)}(\vk-\vk_1,\tau) \eql{sorder}
+%\ee
+
+\section{Quadratic Estimator}\label{sec2}
+In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}.
+Then we forecast the detectability of the quadratic estimator for future surveys.
+Similar to CMB lensing's construction, we can write the general form of the estimator by averaging over pairs of the short-wavelength modes:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1}
+A(\vec{k}_l)=\bigg[\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s')f(\vec{k}_s,\vec{k}_s')  \bigg]^{-1} \eql{a}
 \end{eqnarray}
@@
 \end{eqnarray} 
-Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.\\
-\Sfig{SN}{Detectability of long-wavelength modes. We assume a toy survey of boxsize $8.85\, \rm Gpc$.}
+Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.
+We test that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a} since most of the contribution comes from large $k_s$.
+We will discuss the choice of the upper limit later in section \ref{sec3}.\\
+Assuming the noise is Gaussian, the projected detectability of $P(k_l)$ measurement from the quadratic estimator can be expressed as:
+\be
+\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error}
+\ee
+here $V$ is the volume of a survey and we can compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
+\Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
+We assume a toy survey of boxsize $L=6\, \rm Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
+Moreover, we set the integration range for $\vk_s$ from $0.02 \, \rm Mpc^{-1}$ to $0.15\,\rm Mpc^{-1}$.
+We will see in the next section \ref{sec3} that this choice of the upper limit of integration is very reasonable for our current construction at $z=0$.}
 
-\section{N-Body Simulation}\label{sec3}
+\section{Demonstration with N-Body Simulation}\label{sec3}
 We test the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.

### 2019-10-09 paper/v1.tex
1

@@
 \newcommand{\vs}{\nonumber\\}
+\newcommand{\Var}{\rm Var}
 \newcommand{\vk}{\vec{k}}
@@
 \newcommand{\sfigg}[2]{
-\includegraphics[width=0.9\paperwidth]{../plots/#1}
+\includegraphics[width=0.88\paperwidth]{../plots/#1}
         }
@@
 \newcommand{\peikai}[1]{{\color{blue} #1}}
-\newcommand{\WH}[1]{{\color{red} #1}}
-\newcommand{\wh}[1]{{\color{red} #1}}
 \newcommand{\prvs}[1]{{\color{magenta} #1}}
@@
 This arises physically because small structure structure varies depending on the large scale environment in which it resides.
-This will induce position-dependent clustering in real space and an off-diagonal term in two-point statistics in Fourier space.
+This will induce small scale clustering in real space and an off-diagonal term in two-point statistics in Fourier space.
 Therefore we can build a quadratic estimator for the large scale field.
@@
 Then we compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
-This off-diagonal term proportional to \peikai{with or without an "a"?}long-wavelength mode will be the key factor of constructing the quadratic estimator.
+This off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
 \\
@@
 \end{eqnarray} 
-with $g$ being weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ is defined via $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
+with $g$ being weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ is defined by requiring $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
 \begin{eqnarray}
@@
 \end{eqnarray}
-The Gaussian noise is given by:
+In the absence of shot noise the Gaussian noise is given by:
 \be 
@@
 \section{Demonstration with N-Body Simulation}\label{sec3}
-We test the power of the quadratic estimator using data from snapshot at $z=0$ of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
+We test the power of the quadratic estimator using snapshot at $z=0$ data of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
 Boxsize of BigMDPL is $3.7\,\rm Gpc$.
 We use dark matter particle data to produce matter inhomogeneities.
-Galaxy bias should be considered if we use galaxy catalog.\\
-We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ in Fig.~\rf{hist}.
-$\delta(\vk_l)$ is the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ is the reproduced modes using quadratic estimator \ec{quadest}.\\
+Galaxy bias \cite{Desjacques:2018rev} should be otherwise considered if galaxy or halo catalog is used.\\
+We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ for a 3D grid of $\vk_l$ in Fig.~\rf{hist}.
+$\delta(\vk_l)$ are the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ are the reproduced modes using quadratic estimator \ec{quadest}.\\
 \Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.
@@
 This bias comes from the inaccuracy of second-order perturbation theory.}
-
 Ultimate goal of this approach is to reproduce large scale structure in real space.
-Compare $\delta$ and $\hat{\delta}$ in real space in Fig.~\rf{real} and we can see the quadratic estimator is quite effective for this simulation.
+Compare $\delta$ and $\hat{\delta}$ in real space in Fig.~\rf{real} and we can check the robustness of the quadratic estimator for this simulation.
 \Sfigg{real}{Comparison between $\delta(\vec{x})$ and $\hat{\delta}(\vec{x})$ and their difference.
 The 3D grid of data points are unfolded into 2D grids, $7$ columns corresponds to $7$ slices we have.
-The upper limit of $\vk_s$ is chosen to be $0.15 \, \rm Mpc^{-1}$.}
+The upper limit of $\vk_s$ is chosen to be $0.15 \, \rm Mpc^{-1}$.
+We can compute the signal-to-noise ratio as: $S/N=\Var(\delta)/\Var(\hat{\delta}-\delta)\approx 3$.\peikai{comment?}}
 
@@
 If we try to measure smaller modes, the quadratic estimator approach would be inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
-Our quadratic estimator of long-wavelength modes in this paper is only valid in a box at a given cosmological time.
+Our current formalism of the quadratic estimator for long-wavelength modes in this paper is only valid in a box at a given cosmological time.
 While in photometric redshift surveys we would deal with light cones instead of boxes.
@@
 Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshift, in order to include more nonlinear information.
-When applied to halos or galaxies, this approach can be used to help determine galaxy bias.
-We leave these to future work.
+When applied to halos or galaxies, this approach should be modified to include galaxy bias.
+We leave these to future work.\\
+\\ \\ \\ \\
 

### 2019-10-09 paper/v1.tex
1

@@
 Therefore we can build a quadratic estimator for the large scale field.
-We demonstrate that this quadratic estimator works amazingly well for our N-body simulation test.
+We demonstrate that this quadratic estimator works pretty well with our N-body simulation test.
 
@@
 Method of using small scale position-dependent power spectrum to compute squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
-In order to achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly.
+In order to fully achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly.
 \\
@@
 This can be further related to cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight.
-Similarly in this case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
+Similarly in our case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
 \\
-During CMB lensing quadratic estimator's construction, small scale two-point correlation of CMB temperature modes has off-diagonal terms due to large scale perturbations caused by gravitational lensing.
-The same procedure applies in our case as well - off-diagonal terms of small scale correlations are no-longer zero due to large scale modes.
+During CMB lensing quadratic estimator's construction, small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing.
+The same statistical feature shows up in our case as well -- off-diagonal terms of small scale correlations are no-longer zero due to large scale modes.
 Thus we can create a quadratic estimator for long-wavelength modes using the exact same formalism.
@@
 Then we compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
-This off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
+This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
 \\
@@
 \ee 
-Plugging the perturbative series \ec{pert1} and \ec{pert2} into the fluid equations \ec{fluid1}-\ec{fluid3} after Fourier transform, we can solve second-order density contrast and the result is given by:
+Plugging the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3}, we can solve second-order density contrast and the result is given by:
 \be
@@
 \ee
-Notice \ec{f2} is derived in Einstein-de Sitter universe.
-Nonetheless when we actually do relative calculation in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{f2} throughout the whole work.\\
+Notice \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in Einstein-de Sitter universe.
+Nonetheless when we actually do related calculation in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{pert1} and \ec{f2} throughout the whole work.\\
 Compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order where $\vk_l$ corresponds to a long-wavelength mode we have ($\tau$ is fixed at today):
@@
 
-%Taking the divergence of \ec{eulereq} we can eliminate the gravitational potential $\Phi$ in Fourier space and get evolution equations for $\delta(\vk,\tau)$ and $\theta(\vk,\tau)$ in Fourier space:
-%\bea 
-%\frac{\partial{\delta}}{\partial\tau} + {\theta} &=& -\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12}) \vs
-%&& \times\frac{\vk \cdot \vk_1}{k_1^2}{\theta}(\vk_1,\tau){\delta}(\vk_2,\tau) \eql{fouriercont}\\
-%\frac{\partial{\delta}}{\partial\tau}+\frac{da}{d\tau}\frac{{\theta}}{a}+\frac{6}{\tau^2}{\delta}&=&-\int \frac{d^{3}\vk_{1}}{(2\pi)^3} \int \frac{d^{3}\vk_{2}}{(2\pi)^3} (2\pi)^3 \delta_{\rm D}(\vk-\vk_{12})\vs
-%&&\times \frac{k^2(\vk_1 \cdot \vk_2)}{2k_1^2 k_2^2} {\theta}(\vk_1,\tau){\theta}(\vk_2,\tau) \eql{fouriereuler}
-%\eea
-%here $\vk_{12}=\vk_1 +\vk_2$ and more generally $\vk_{1\cdots n}=\vk_1 + \cdots +\vk_n$; $\theta\equiv \vec{\nabla}\cdot \vec{v}$ is the divergence of velocity field.\\
-%In Einstein-de Sitter space, linear growth function $D_{1}(a)=a$ and we can solve these equations perturbatively using expansion:
-%\bea
-%{\delta}(\vk,\tau)&=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}a^{n}(\tau)\delta_{n}(\vk) \\ {\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)=-H(\tau)%\sum_{n=1}^{\infty}a^{n+1}(\tau)\theta_{n}(\vk)
-%\eea
-%\\where the superscript $(n)$ means the order of perturbation theory, and first order term ${\delta}^{(1)}$ corresponds to linear evolution.
-Linear power spectrum is given by this first order term via:
-%\be 
-%\langle {\delta}(\vk){\delta}(\vk') \rangle =(2\pi)^3 \delta_{\rm D}(\vk+\vk')P_{\rm lin}(k) \eql{lin}
-%\ee 
-%Substituting the two perturbative series into \ec{fouriercont} and \ec{fouriereuler} we get recursion relations for ${\delta}_{n}(\vk)$ and ${\theta}_{n}(\vk)$ with solution:
-%\bea
-%{\delta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
-%&&\times F_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n}) \\
-%{\theta}_{n}(\vk) &=& \int \frac{d^{3}\vk_{1}}{(2\pi)^3} \cdots \int \frac{d^{3}\vk_{n}}{(2\pi)^3}(2\pi)^3 \delta_{\rm D} (\vk-\vk_{1\cdots n}) \vs
-%&&\times G_{n}(\vk_1,\cdots,\vk_n){\delta}_1(\vk_{1}) \cdots {\delta}_1(\vk_{n})
-%\eea
-%and recursion relations are encoded in kernels $F_n$ and $G_n$. Since we only consider up to second-order, the second-order symmetrized kernels are given by:
-%\bea 
-%F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}) \\
-%G_{2}(\vk_1,\vk_2)=\frac{3}{7}+\frac{4}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})
-%\eea 
-%This approach gives a nearly accurate description of $\Lambda$CDM universe \cite{Takahashi:2008to} with slight generalization \cite{Bernardeau:2002rev}:
-%\bea
-%{\delta}(\vk,\tau) &=&\sum_{n=1}^{\infty} {\delta}^{(n)}(\vk,\tau)=\sum_{n=1}^{\infty}D_1^{n}(\tau)\delta_{n}(\vk) \\
-%{\theta}(\vk,\tau)&=&\sum_{n=1}^{\infty}{\theta}^{(n)}(\vk,\tau)\vs
-%&=&-\frac{d\,\ln D_1(\tau)}{d\tau}\sum_{n=1}^{\infty}D_1^{n}(\tau)\theta_{n}(\vk) 
-%\eea
-%Time-dependent second-order density contrast can be expressed as convolution of two linear density fields with kernel $F_2$:
-%\be 
-%{\delta}^{(2)}(\vk,\tau)=\int \frac{d^{3}\vk_{1}}{(2\pi)^3} F_2(\vk_1,\vk-\vk_1){\delta}^{(1)}(\vk_1,\tau) {\delta}^{(1)}(\vk-\vk_1,\tau) \eql{sorder}
-%\ee
-
 \section{Quadratic Estimator}\label{sec2}
@@
 $\delta(\vk_l)$ are the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ are the reproduced modes using quadratic estimator \ec{quadest}.\\
-\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.
-We can see that in the weakly nonlinear regime, left plot peaks at $1$ which is what we would expect.
+\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.\peikai{should be more clear what does it count..} We can see that in the weakly nonlinear regime, left plot peaks at $1$ which is what we would expect.
 While for the right plot, when we go higher into nonlinear scale, ratio peak at about $1.3$.

### 2019-10-09 paper/v1.tex
1

@@
 Notice \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in Einstein-de Sitter universe.
-Nonetheless when we actually do related calculation in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{pert1} and \ec{f2} throughout the whole work.\\
+Nonetheless when we actually do related calculations in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{pert1} and \ec{f2} throughout the whole work.\\
 Compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order where $\vk_l$ corresponds to a long-wavelength mode we have ($\tau$ is fixed at today):
@@
 \eea 
-We claim that generally correlation function of three Gaussian fields is nonzero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
+\peikai{Need to rephrase (don't know how): We claim that generally correlation function of three Gaussian fields is non-zero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
 \be 
@@
 The above equation is true since in a real life survey, we can only measure this long-wavelength mode very limited times.
-Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.\\
+Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.}\\
 We can do this contraction twice in this integral \ec{integral}.
@@
 \eea 
-where we use the fact that $F_2$ is symmetric function. Finally we have:
+where we use the fact that $F_2$ is a symmetric function. Finally we have:
 \be 

### 2019-10-09 paper/v1.tex
1

@@
 \ee 
-Plugging the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3}, we can solve second-order density contrast and the result is given by:
+Plugging the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3}, we can solve the second-order density contrast and the result is given by:
 \be
@@
 $\delta(\vk_l)$ are the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ are the reproduced modes using quadratic estimator \ec{quadest}.\\
-\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.\peikai{should be more clear what does it count..} We can see that in the weakly nonlinear regime, left plot peaks at $1$ which is what we would expect.
-While for the right plot, when we go higher into nonlinear scale, ratio peak at about $1.3$.
-This bias comes from the inaccuracy of second-order perturbation theory.}
+\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.\peikai{should be more clear what does it count..} We can see that the right plot is more biased due to inaccuracy of second-order SPT when we go higher into nonlinear scale.}
 Ultimate goal of this approach is to reproduce large scale structure in real space.
@@
 The upper limit of $\vk_s$ is chosen to be $0.15 \, \rm Mpc^{-1}$.
-We can compute the signal-to-noise ratio as: $S/N=\Var(\delta)/\Var(\hat{\delta}-\delta)\approx 3$.\peikai{comment?}}
+We can compute the signal-to-noise ratio as: $S/N=\Var(\delta)/\Var(\hat{\delta}-\delta)\approx 3$.
+\peikai{comment?}}
 

### 2019-10-15 paper/v1.tex
Some suggested things to add + some light editing

@@
 \definecolor{darkgreen}{cmyk}{0.85,0.1,1.00,0} 
+\definecolor{darkorange}{rgb}{1.0,0.2,0.0}
 \newcommand{\scott}[1]{{\color{darkgreen} #1}}
@@
 \newcommand{\nl}{\\ \indent}
+\newcommand{\RC}[1]{{\color{darkorange} #1}}
 \begin{document}
@@
   \noindent Large scale density modes cannot be measured directly through surveys but we can study them by measuring perturbations on small scales.
+\RC{ Should really say instead something about  the fact that large scale modes are difficult to measure
+    because they are sensitive to systematic observational  errors in
+    galaxy surveys - not that they can't be measured}
   Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
-This arises physically because small structure structure varies depending on the large scale environment in which it resides.
-This will induce small scale clustering in real space and an off-diagonal term in two-point statistics in Fourier space.
-Therefore we can build a quadratic estimator for the large scale field.
-We demonstrate that this quadratic estimator works pretty well with our N-body simulation test.
+This arises physically because the growth of small scale structures varies depending on the large scale environment in which they reside.
+This induces small scale clustering in real space and an off-diagonal term in the two-point statistics in Fourier space.
+We can therefore build a quadratic estimator for the large scale field.
+We demonstrate that this quadratic estimator works well with an N-body simulation test \RC{what do we find?
+scales?
++ final
+    speculative sentence
+    about potential of method to do cosmology}.
 
@@
 Measuring the distribution of structures on large scales has been one of the main goals of recent surveys despite it is hard to accomplish directly.
-To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
-Method of using small scale position-dependent power spectrum to compute squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
+\RC{Should include brief examples of why it is very interesting - for example
+  to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting}
+To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
+The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
 In order to fully achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly.
 \\
-Starting from second-order standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
-This can be further related to cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where CMB temperature field has a second-order correction due to gravitational field along line of sight.
-Similarly in our case the short-wavelength mode's nonlinear terms are related to the large scale environment it belongs to.
+Starting from second-order standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
+This can be further related to the cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
+Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.
 \\
-During CMB lensing quadratic estimator's construction, small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing.
-The same statistical feature shows up in our case as well -- off-diagonal terms of small scale correlations are no-longer zero due to large scale modes.
-Thus we can create a quadratic estimator for long-wavelength modes using the exact same formalism.
+The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing.
+The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no-longer zero, due to the effect of large scale modes.
+Thus we can create a quadratic estimator for long-wavelength modes using exactly the same formalism.
 \\
 We begin with a brief review of SPT up to second-order in section \ref{sec1}.
-Then we build the quadratic estimator and compute the detectability of the estimator in section \ref{sec2}.
+We then build the quadratic estimator and compute the detectability of the estimator in section \ref{sec2}.
 In section \ref{sec3} we present a concise study of the estimator with data from N-body simulation.
@@
 In this section we review the SPT approach which describes small scale nonlinearity.
-Then we compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
+\RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter. Stating this explicitly could
+be helpful for a reader.} 
+We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
 This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
@@
 \eea
-where $D_1$ is the linear growth factor. The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The inear power spectrum is given by this first order term via:
+where $D_1$ is the linear growth factor \RC{define this e.g.
+$\delta(\tau)=D_{1}\delta(0)$}.
+The first order term ${\delta}^{(1)}$ corresponds to linear evolution.
+The linear power spectrum is given by this first order term via:
 \be 
@@
 \ee 
-Plugging the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3}, we can solve the second-order density contrast and the result is given by:
+Substituting the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3}, we can solve for the second-order density contrast:
 \be
@@
 \ee
-Notice \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in Einstein-de Sitter universe.
-Nonetheless when we actually do related calculations in $\Lambda$CDM universe, the difference is negligible \cite{Takahashi:2008to} thus we still use the expression from \ec{pert1} and \ec{f2} throughout the whole work.\\
-Compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ up to second-order where $\vk_l$ corresponds to a long-wavelength mode we have ($\tau$ is fixed at today):
+Note that \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in an Einstein-de Sitter universe.
+Nonetheless for related calculations in a $\Lambda$CDM universe, the difference is found to be negligible \cite{Takahashi:2008to}, and thus we use the expressions from \ec{pert1} and \ec{f2} throughout this work.\\
+We next compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ \RC{why is this squeezed limit - is $\vk_s,\vk_s' \gg \vk_l$?}, up to second-order.
+Here $\vk_l$ corresponds to a long-wavelength mode, and $\tau$  is at the present day:
 \bea 
@@
 Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.}\\
-We can do this contraction twice in this integral \ec{integral}.
-One occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, we can extract ${\delta}^{(1)}(\vk)$ out; the other one occurs when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\
-Use \ec{lin} the integral in \ec{integral} can be evaluated as:
+
+\RC{Maybe this?: The RHS of \ec{integral} includes an integral over the
+  three point
+  correlation function of modes of a Gaussian field. If one of the modes has
+  a  much longer wavelength than the others, then its contribution will be
+  limited to a few examples, and
+  a statistical average will not take place.  In this case, we can
+  move the long
+  wavelength mode outside the  bracket, so that the following is a
+  good approximation:
+\be 
+\langle
+\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
+{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
+\rangle
+=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction},
+\ee 
+where $\vk_1$ and $\vk_2$ are two short modes and $\vk_3$ is the long
+mode.
+}
+
+We can use this contraction twice in \ec{integral}.
+One use occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, when we can extract ${\delta}^{(1)}(\vk)$; the other is when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\
+Using \ec{lin}, \ec{integral} can be evaluated as:
 \bea 
@@
 \eea 
-where we use the fact that $F_2$ is a symmetric function. Finally we have:
+where we take advantage of the fact that $F_2$ is a symmetric function.
+Finally we have:
 \be 
@@
 \ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.
-Also notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.
+\RC{Move this sentence to \ref{sec3}: Also notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.}
 
@@
 In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}.
-Then we forecast the detectability of the quadratic estimator for future surveys.
-Similar to CMB lensing's construction, we can write the general form of the estimator by averaging over pairs of the short-wavelength modes:
+We then forecast the detectability of the quadratic estimator for future surveys.
+As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
 \begin{eqnarray}
-\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest}
+\hat{\delta}^{(1)}(\vec{k}_l)=A(\vec{k}_l)\int \frac{d^3 \vec{k}_s}{(2\pi)^3} g(\vec{k}_s,\vec{k}_s'){\delta}(\vec{k}_s){\delta}(\vec{k}_s') \eql{quadest},
 \end{eqnarray} 
-with $g$ being weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ is defined by requiring $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
+with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$  defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-Noise term reduces simply to $N(\vk_l)=A(\vk_l)$.
-We test that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a} since most of the contribution comes from large $k_s$.
-We will discuss the choice of the upper limit later in section \ref{sec3}.\\
-Assuming the noise is Gaussian, the projected detectability of $P(k_l)$ measurement from the quadratic estimator can be expressed as:
+The noise term reduces simply to $N(\vk_l)=A(\vk_l)$.
+We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$.
+We  discuss the choice of the upper limit later, in section \ref{sec3}.\\
+Assuming Gaussian noise, the projected detectability of a $P(k_l)$ measurement using the quadratic estimator can be expressed as:
 \be
-\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error}
+\frac{1}{\sigma^{2}(k_l)}=\frac{V k_l^2 \Delta k }{(2\pi)^2}\bigg[\frac{P_{\rm lin}(k_l)}{P_{\rm lin}(k_l)+N(k_l) }\bigg]^2 \eql{error},
 \ee
-here $V$ is the volume of a survey and we can compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
+where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of
+  sentences about Figure 1, bearing in mind that you have put information in
+  the caption already. Also remember to change the survey volume to
+match DESI and state this.}
+
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
@@
 Moreover, we set the integration range for $\vk_s$ from $0.02 \, \rm Mpc^{-1}$ to $0.15\,\rm Mpc^{-1}$.
-We will see in the next section \ref{sec3} that this choice of the upper limit of integration is very reasonable for our current construction at $z=0$.}
+\RC{Put this in the main text: We will see in the next section \ref{sec3} that this choice of the upper limit of integration is very reasonable for our current construction at $z=0$.}}
 
-\section{Demonstration with N-Body Simulation}\label{sec3}
-We test the power of the quadratic estimator using snapshot at $z=0$ data of BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
-Boxsize of BigMDPL is $3.7\,\rm Gpc$.
-We use dark matter particle data to produce matter inhomogeneities.
-Galaxy bias \cite{Desjacques:2018rev} should be otherwise considered if galaxy or halo catalog is used.\\
-We use nbodykit code to get Fourier density modes \cite{Hand:2018nby} and compare $\delta(\vk_l)$ with $\hat{\delta}(\vk_l)$ for a 3D grid of $\vk_l$ in Fig.~\rf{hist}.
-$\delta(\vk_l)$ are the long-wavelength modes we get directly from N-body simulation and $\hat{\delta}(\vk_l)$ are the reproduced modes using quadratic estimator \ec{quadest}.\\
-\Sfig{hist}{Histogram of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ in Fourier space with different integration range of $k_s$.\peikai{should be more clear what does it count..} We can see that the right plot is more biased due to inaccuracy of second-order SPT when we go higher into nonlinear scale.}
-Ultimate goal of this approach is to reproduce large scale structure in real space.
-Compare $\delta$ and $\hat{\delta}$ in real space in Fig.~\rf{real} and we can check the robustness of the quadratic estimator for this simulation.
-\Sfigg{real}{Comparison between $\delta(\vec{x})$ and $\hat{\delta}(\vec{x})$ and their difference.
-The 3D grid of data points are unfolded into 2D grids, $7$ columns corresponds to $7$ slices we have.
-The upper limit of $\vk_s$ is chosen to be $0.15 \, \rm Mpc^{-1}$.
-We can compute the signal-to-noise ratio as: $S/N=\Var(\delta)/\Var(\hat{\delta}-\delta)\approx 3$.
-\peikai{comment?}}
+\section{Demonstration with an N-Body Simulation}\label{sec3}
+We test the power of the quadratic estimator using data from a cosmological
+N-body simulation.
+We use the $z=0$ snapshot from BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
+The cubical box side length of BigMDPL is $3.7\,\rm Gpc$.
+We use the dark matter particle data to compute
+the matter density field, leaving the effect of using galaxies or halos to
+trace the field \cite{Desjacques:2018rev} to  future work.\\
+We use the code nbodykit \cite{Hand:2018nby} 
+to measure the Fourier density modes, and \ec{quadest} to estimate the
+long wavelength modes  from the measured short wavelength modes. 
+How well the estimator works can be seen from Fig.~\rf{hist}, where we show
+histograms of the ratio of the estimated mode amplitudes ($\hat{\delta}(\vk_l)$) to their true amplitudes ($\delta(\vk_l)$). The
+two panels show the differences between a short wavelength mode cutoff of $k_s=0.15 \rm Mpc^{1}$
+and  $k_s=0.25 \rm Mpc^{1}$ \RC{Comment on what the figure shows - for example individual mode amplitudes are unbiased when $k_s=
+  0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this
+  here from fig caption:
+We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are
+biased (the mode is $\sim 20
+\%$ too high)
+due to the increasing inaccuracy of second-order SPT as we move into 
+nonlinear scales}
+\Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
+Another goal of this approach is to reproduce large scale structure in real space. To test this, we compute real space density fields by taking the
+inverse transform
+of both the directly measured long wavelength Fourier modes and
+the long wavelength modes
+predicted using the quadratic estimator. These density fields, $\delta$ and $\hat{\delta}$ respectively are plotted in Fig.~\rf{real}. We can see that...
+\RC{describe how well it works based on what we can see in the figure}
+
+\Sfig{real}{\RC{Sadly this figure can't really be two columns in a PRL - there isn't enough room.
+I think you should put it back to one column, but moving the color scale to the bottom or top would allow you to fill the column a bit better} Comparison of the true density field in
+  the BigMPDL simulation ($\delta(\vec{x})$ computed using the
+  directly measured large-scale modes, top row) and the density
+  field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
+  The bottom row shows their difference. Each panel represents a slice through
+  the simulation volume,  $3.7\,\rm Gpc$ wide, and
+  one cell ($0.5\,\rm Gpc$) thick.  The upper limit of $\vk_s$ was $0.15 \, \rm Mpc^{-1}$. \RC{As discussed, remove this reference to
+  S/N: We can compute the signal-to-noise ratio as: $S/N=\Var(\delta)/\Var(\hat{\delta}-\delta)\approx 3$. \peikai{comment?}}}
 
 \section{Conclusion}\label{sec4}
-In this paper, we have proposed a new and powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
-The noise term $N=A$ would reduce significantly if we go higher into nonlinear regime while second-order SPT is no longer accurate in this case.
-Thus if we want to detect even larger scales, we might need to use contributions from higher order perturbations and expand the integration range to reduce noise level.
+In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
+\RC{ State that this is good because we won't be sensitive to
+  observational systematics, sky gradients, dust etc}
+\RC{Give a short list of cool things we can do, with references: measure 3D clustering
+  beyond the matter radiation equality turnover for the first time,
+  look for evidence of general relativistic effects which are strongest
+  on large scales (e.g., https://journals.aps.org/prd/abstract/10.1103/PhysRevD.85.023504 ), look for evidence of large scale anomalies, like in the CMB,
+  constrain non-Gaussianity, 
+  etc }
+
+Extensions of our work suggest themselves and will be
+relevant to attempts to apply it to observational data.
+The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case.
+Thus, to detect even larger scales, we may need to use contributions from higher order perturbations and expand the integration range to reduce the noise level.
 \\
-Another concern is the range of long-wavelength modes we are able to detect.
-In the N-body simulation, we use $k_l$ from largest possible mode $1.7 \times 10^{-3} \, \rm Mpc^{-1}$ to $8.9\times 10^{-3} \, \rm Mpc^{-1}$.
-If we try to measure smaller modes, the quadratic estimator approach would be inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
-Our current formalism of the quadratic estimator for long-wavelength modes in this paper is only valid in a box at a given cosmological time.
-While in photometric redshift surveys we would deal with light cones instead of boxes.
-Thus we expect the expression for the quadratic estimator to be generalized for photometric surveys.
-Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshift, in order to include more nonlinear information.
-When applied to halos or galaxies, this approach should be modified to include galaxy bias.
-We leave these to future work.\\
+Another issue relates to the range of long-wavelength modes that are detectable. In the N-body simulation,  $k_l$ for modes recovered ranged from
+$1.7 \times 10^{-3} \, \rm Mpc^{-1}$ to $8.9\times 10^{-3} \, \rm Mpc^{-1}$.
+If we try to measure smaller modes, the quadratic estimator approach would
+become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
+Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time. As the length
+scales are so large, a more realistic situation should deal with
+observations on the light cone.
+The expression for the quadratic estimator to be generalized to take this into account.
+Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information.
+Finally, when applied to datasets consisting of
+halos or galaxies, the approach should be modified to include galaxy bias. We
+also leave this to future work.\\ 
 \\ \\ \\ \\
@@
 \acknowledgements
-\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  SD, PL and RC were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.\\
-The BigMDPL simulation has been performed at LRZ Munich within the PRACE project pr86bu.
+\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.
+SD, PL and RC were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
+SD and RC also acknowledge support from NSF AST-1909193\\
+The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu.
 The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).

### 2019-10-16 paper/v1.tex
1

@@
 \newcommand{\sfigg}[2]{
-\includegraphics[width=0.88\paperwidth]{../plots/#1}
+\includegraphics[width=0.424\paperwidth]{../plots/#1}
         }
@@
 \newcommand{\Sfigg}[2]{
-   \begin{figure*}[thbp]
+   \begin{figure}[thbp]
     \sfigg{../plots/#1.pdf}{\columnwidth}
@@
     \label{fig:#1}
-   \end{figure*}
+   \end{figure}
 }
@@
 \newcommand{\MR}[1]{{\color{blue} MR: #1}}
+\newcommand{\RC}[1]{{\color{darkorange} #1}}
 \newcommand{\nl}{\\ \indent}
-\newcommand{\RC}[1]{{\color{darkorange} #1}}
 \begin{document}
@@
 \begin{abstract}
-  \noindent Large scale density modes cannot be measured directly through surveys but we can study them by measuring perturbations on small scales.
-\RC{ Should really say instead something about  the fact that large scale modes are difficult to measure
-    because they are sensitive to systematic observational  errors in
-    galaxy surveys - not that they can't be measured}
-  Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
+\noindent \peikai{Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them by measuring perturbations on small scales.} \RC{Should really say instead something about  the fact that large scale modes are difficult to measure because they are sensitive to systematic observational  errors in galaxy surveys - not that they can't be measured.} Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
 This arises physically because the growth of small scale structures varies depending on the large scale environment in which they reside.
@@
 scales?
-+ final
-    speculative sentence
-    about potential of method to do cosmology}.
++ final speculative sentence about potential of method to do cosmology}.
+\peikai{We find this quadratic estimator very powerful for reconstructing long-wavelength modes with the $(2.5\,h^{-1}\,\rm Gpc)^3$ box.
+It provides us with a novel way of studying large scale structure and topics related.}
 
@@
 \section{Introduction}
-Measuring the distribution of structures on large scales has been one of the main goals of recent surveys despite it is hard to accomplish directly.
-\RC{Should include brief examples of why it is very interesting - for example
-  to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting}
-To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
+Measuring the distribution of structures on large scales has been one of the main goals of recent surveys\peikai{, through which we can have a better constraint of $f_{\rm NL}$ or solve large scale anomalies,} despite it is hard to accomplish directly.\RC{Should include brief examples of why it is very interesting - for example to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting} To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
 The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
@@
 This can be further related to the cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
-Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.
-\\
+Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.\\
 The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing.
@@
 In this section we review the SPT approach which describes small scale nonlinearity.
-\RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter. Stating this explicitly could
-be helpful for a reader.} 
-We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
+\RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter.
+Stating this explicitly could be helpful for a reader.} \peikai{See also \cite{Bernardeau:2002rev} for a detailed derivation.} We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
 This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
@@
 where $D_1$ is the linear growth factor \RC{define this e.g.
-$\delta(\tau)=D_{1}\delta(0)$}.
+$\delta(\tau)=D_{1}\delta(0)$} \peikai{defined by $\delta^{(1)}(\vk,\tau)=D_{1}(\tau)\delta_{0}(\vk)$ with $\delta_0$ being the initial density field.
+Is it necessary?
+This equation is already indicated in Eq(4).}.
 The first order term ${\delta}^{(1)}$ corresponds to linear evolution.
@@
 Nonetheless for related calculations in a $\Lambda$CDM universe, the difference is found to be negligible \cite{Takahashi:2008to}, and thus we use the expressions from \ec{pert1} and \ec{f2} throughout this work.\\
-We next compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ \RC{why is this squeezed limit - is $\vk_s,\vk_s' \gg \vk_l$?}, up to second-order.
+We next compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ \RC{why is this squeezed limit - is $\vk_s,\vk_s' \gg \vk_l$?}\peikai{with $\vk_s,\vk_s' \gg \vk_l$} up to second-order.
 Here $\vk_l$ corresponds to a long-wavelength mode, and $\tau$  is at the present day:
 \bea 
-&& \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{\vk_s+\vk_s'=\vk_l}
-\vs 
+&& \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{\vk_s+\vk_s'=\vk_l}\vs
 &=&  \langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(2)}(\vec{k}_s') \rangle+\langle {\delta}^{(2)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s') \rangle
@@
 Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.}\\
-
-\RC{Maybe this?: The RHS of \ec{integral} includes an integral over the
-  three point
-  correlation function of modes of a Gaussian field. If one of the modes has
-  a  much longer wavelength than the others, then its contribution will be
-  limited to a few examples, and
-  a statistical average will not take place.  In this case, we can
-  move the long
-  wavelength mode outside the  bracket, so that the following is a
-  good approximation:
+\RC{Maybe this?: The RHS of \ec{integral} includes an integral over the three point correlation function of modes of a Gaussian field.
+If one of the modes has a much longer wavelength than the others, then its contribution will be limited to a few examples, and a statistical average will not take place.
+In this case, we can move the long wavelength mode outside the bracket, so that the following is a good approximation:
 \be 
@@
 \ee 
-where $\vk_1$ and $\vk_2$ are two short modes and $\vk_3$ is the long
-mode.
-}
-
+where $\vk_1$ and $\vk_2$ are two short modes and $\vk_3$ is the long mode.}\\
 We can use this contraction twice in \ec{integral}.
@@
 &&\int \frac{d^3\vec{k}}{(2\pi)^3} F_2 (\vec{k},\vec{k}_s'-\vec{k})\langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s'-\vec{k}){\delta}^{(1)}(\vec{k}) \rangle \vs
-&=&\int d^3\vk F_2(\vec{k},\vec{k}_s'-\vec{k}) \delta_{\rm D}(\vk_s+\vk_s'-\vk)P_{\rm 
-lin}(k_s){\delta}^{(1)}(\vec{k}) \vs
-&+&\int d^3\vk F_2(\vec{k},\vec{k}_s'-\vec{k}) \delta_{\rm D}(\vk_s+\vk)P_{\rm 
-lin}(k_s){\delta}^{(1)}(\vk_s'-\vk) \vs
+&=&\int d^3\vk F_2(\vec{k},\vec{k}_s'-\vec{k}) \delta_{\rm D}(\vk_s+\vk_s'-\vk)P_{\rm lin}(k_s){\delta}^{(1)}(\vec{k}) \vs
+&+&\int d^3\vk F_2(\vec{k},\vec{k}_s'-\vec{k}) \delta_{\rm D}(\vk_s+\vk)P_{\rm lin}(k_s){\delta}^{(1)}(\vk_s'-\vk) \vs
 &=&2F_2(-\vk_s,\vk_s+\vk_s')P_{\rm lin}(k_s){\delta}^{(1)}(\vk_s+\vk_s')
 \eea 
-where we take advantage of the fact that $F_2$ is a symmetric function.
+where we take advantage of the fact that $F_2$ is a symmetric function.\\
 Finally we have:
@@
 \ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.
-\RC{Move this sentence to \ref{sec3}: Also notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator, we can see this effect in \ref{sec3}.}
 
@@
 \ee
-where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of
-  sentences about Figure 1, bearing in mind that you have put information in
-  the caption already. Also remember to change the survey volume to
-match DESI and state this.}
-
+where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already.
+Also remember to change the survey volume to match DESI and state this.} \peikai{We show the projected error of long-wavelength power spectrum using this quadratic estimator with fiducial value $1$.
+The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$.
+We will see in the next section \ref{sec3} that this choice of the upper limit is very reasonable for our current construction at $z=0$.
+Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$ case).}\\
+\peikai{plot linear or nonlinear? Change ylabel?}
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
-We assume a toy survey of boxsize $L=6\, \rm Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
-Moreover, we set the integration range for $\vk_s$ from $0.02 \, \rm Mpc^{-1}$ to $0.15\,\rm Mpc^{-1}$.
-\RC{Put this in the main text: We will see in the next section \ref{sec3} that this choice of the upper limit of integration is very reasonable for our current construction at $z=0$.}}
+We assume a toy survey of boxsize $L=4\, h\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
+Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}
 
 \section{Demonstration with an N-Body Simulation}\label{sec3}
-We test the power of the quadratic estimator using data from a cosmological
-N-body simulation.
+We test the power of the quadratic estimator using data from a cosmological N-body simulation.
 We use the $z=0$ snapshot from BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
 The cubical box side length of BigMDPL is $3.7\,\rm Gpc$.
-We use the dark matter particle data to compute
-the matter density field, leaving the effect of using galaxies or halos to
-trace the field \cite{Desjacques:2018rev} to  future work.\\
-We use the code nbodykit \cite{Hand:2018nby} 
-to measure the Fourier density modes, and \ec{quadest} to estimate the
-long wavelength modes  from the measured short wavelength modes. 
-How well the estimator works can be seen from Fig.~\rf{hist}, where we show
-histograms of the ratio of the estimated mode amplitudes ($\hat{\delta}(\vk_l)$) to their true amplitudes ($\delta(\vk_l)$). The
-two panels show the differences between a short wavelength mode cutoff of $k_s=0.15 \rm Mpc^{1}$
-and  $k_s=0.25 \rm Mpc^{1}$ \RC{Comment on what the figure shows - for example individual mode amplitudes are unbiased when $k_s=
-  0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this
-  here from fig caption:
-We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are
-biased (the mode is $\sim 20
-\%$ too high)
-due to the increasing inaccuracy of second-order SPT as we move into 
-nonlinear scales}
+We use the dark matter particle data to compute the matter density field, leaving the effect of using galaxies or halos to trace the field \cite{Desjacques:2018rev} to  future work.\\
+We use the code nbodykit \cite{Hand:2018nby} to measure the Fourier density modes, and \ec{quadest} to estimate the long wavelength modes  from the measured short wavelength modes.
+How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$.
+The two panels show the differences between a short wavelength mode cutoff of $k_s=0.22\, h\, \rm Mpc^{-1}$ and  $k_s=0.37\,h\, \rm Mpc^{-1}$.
+\peikai{Notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator.
+As we can see in this plot that individual mode amplitudes are basically unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$.
+While for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are more biased (the center of the ratio $\sim 20 \%$ too high) and more incorrect (about $\sim 50 \%$ of the modes have negative real parts of $\delta/\hat{\delta}$) due to the increasing inaccuracy of second-order SPT.
+} \RC{Comment on what the figure shows -  for example individual mode amplitudes are unbiased when $k_s= 0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this here from fig caption: We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are biased (the mode is $\sim 20 \%$ too high) due to the increasing inaccuracy of second-order SPT as we move into nonlinear scales}
 \Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
-Another goal of this approach is to reproduce large scale structure in real space. To test this, we compute real space density fields by taking the
-inverse transform
-of both the directly measured long wavelength Fourier modes and
-the long wavelength modes
-predicted using the quadratic estimator. These density fields, $\delta$ and $\hat{\delta}$ respectively are plotted in Fig.~\rf{real}. We can see that...
+\\Another goal of this approach is to reproduce large scale structure in real space.
+To test this, we compute real space density fields by taking the inverse transform of both the directly measured long wavelength Fourier modes and the long wavelength modes predicted using the quadratic estimator.
+These density fields, $\delta$ and $\hat{\delta}$ respectively are plotted in Fig.~\rf{real}.
+We can see that \peikai{our quadratic estimator }
 \RC{describe how well it works based on what we can see in the figure}
-
-\Sfig{real}{\RC{Sadly this figure can't really be two columns in a PRL - there isn't enough room.
-I think you should put it back to one column, but moving the color scale to the bottom or top would allow you to fill the column a bit better} Comparison of the true density field in
-  the BigMPDL simulation ($\delta(\vec{x})$ computed using the
-  directly measured large-scale modes, top row) and the density
-  field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
-  The bottom row shows their difference. Each panel represents a slice through
-  the simulation volume,  $3.7\,\rm Gpc$ wide, and
-  one cell ($0.5\,\rm Gpc$) thick.  The upper limit of $\vk_s$ was $0.15 \, \rm Mpc^{-1}$. \RC{As discussed, remove this reference to
-  S/N: We can compute the signal-to-noise ratio as: $S/N=\Var(\delta)/\Var(\hat{\delta}-\delta)\approx 3$. \peikai{comment?}}}
+\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
+The bottom row shows their difference.
+Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.
+The upper limit of $\vk_s$ was $0.22 \,h\, \rm Mpc^{-1}$.}
 
@@
 In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
-\RC{ State that this is good because we won't be sensitive to
-  observational systematics, sky gradients, dust etc}
-\RC{Give a short list of cool things we can do, with references: measure 3D clustering
-  beyond the matter radiation equality turnover for the first time,
-  look for evidence of general relativistic effects which are strongest
-  on large scales (e.g., https://journals.aps.org/prd/abstract/10.1103/PhysRevD.85.023504 ), look for evidence of large scale anomalies, like in the CMB,
-  constrain non-Gaussianity, 
-  etc }
-
-Extensions of our work suggest themselves and will be
-relevant to attempts to apply it to observational data.
+\RC{ State that this is good because we won't be sensitive to observational systematics, sky gradients, dust etc}
+\RC{Give a short list of cool things we can do, with references: measure 3D clustering beyond the matter radiation equality turnover for the first time, look for evidence of general relativistic effects which are strongest on large scales (e.g., \cite{Jeong:2012ls}), look for evidence of large scale anomalies, like in the CMB, constrain non-Gaussianity,  etc }\\
+Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data.
 The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case.
@@
 \\
-Another issue relates to the range of long-wavelength modes that are detectable. In the N-body simulation,  $k_l$ for modes recovered ranged from
-$1.7 \times 10^{-3} \, \rm Mpc^{-1}$ to $8.9\times 10^{-3} \, \rm Mpc^{-1}$.
-If we try to measure smaller modes, the quadratic estimator approach would
-become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
-Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time. As the length
-scales are so large, a more realistic situation should deal with
-observations on the light cone.
+Another issue relates to the range of long-wavelength modes that are detectable.
+In the N-body simulation,  $k_l$ for modes recovered ranged from $1.7 \times 10^{-3} \, \rm Mpc^{-1}$ to $8.9\times 10^{-3} \, \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
+Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time.
+As the length scales are so large, a more realistic situation should deal with observations on the light cone.
 The expression for the quadratic estimator to be generalized to take this into account.
 Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information.
-Finally, when applied to datasets consisting of
-halos or galaxies, the approach should be modified to include galaxy bias. We
-also leave this to future work.\\ 
-\\ \\ \\ \\
+Finally, when applied to datasets consisting of halos or galaxies, the approach should be modified to include galaxy bias.
+We also leave this to future work.\\
 
@@
 \noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.
-SD, PL and RC were supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
-SD and RC also acknowledge support from NSF AST-1909193\\
+SD, PL and RC are supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
+SD and RC also acknowledge support from NSF AST-1909193.\\
 The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu.
 The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
+
 %\input{main.bbl}
+
 \bibliography{refs}

### 2019-10-16 paper/v1.tex
1

@@
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
-We assume a toy survey of boxsize $L=4\, h\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
+We assume a toy survey of boxsize $L=4\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
 Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}
@@
 We use the $z=0$ snapshot from BigMPDL, one of the MultiDark cosmological simulations \cite{Klypin:2014nov}.
-The cubical box side length of BigMDPL is $3.7\,\rm Gpc$.
+The cubical box side length of BigMDPL is $2.5\,h^{-1}\,\rm Gpc$.
 We use the dark matter particle data to compute the matter density field, leaving the effect of using galaxies or halos to trace the field \cite{Desjacques:2018rev} to  future work.\\
 We use the code nbodykit \cite{Hand:2018nby} to measure the Fourier density modes, and \ec{quadest} to estimate the long wavelength modes  from the measured short wavelength modes.
-How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$.
+How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$ \peikai{for different values of $\vk_l$}.
 The two panels show the differences between a short wavelength mode cutoff of $k_s=0.22\, h\, \rm Mpc^{-1}$ and  $k_s=0.37\,h\, \rm Mpc^{-1}$.
@@
 Another issue relates to the range of long-wavelength modes that are detectable.
-In the N-body simulation,  $k_l$ for modes recovered ranged from $1.7 \times 10^{-3} \, \rm Mpc^{-1}$ to $8.9\times 10^{-3} \, \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
+In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
 Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time.

### 2019-10-17 paper/v1.tex
1

@@
 + final speculative sentence about potential of method to do cosmology}.
-\peikai{We find this quadratic estimator very powerful for reconstructing long-wavelength modes with the $(2.5\,h^{-1}\,\rm Gpc)^3$ box.
+\peikai{We find this quadratic estimator very powerful for reconstructing long-wavelength modes with the $(2.5\,h^{-1}\,\rm Gpc)^3$ simulation.
 It provides us with a novel way of studying large scale structure and topics related.}
@@
 Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
-We use flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
+We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
 
@@
 \RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter.
-Stating this explicitly could be helpful for a reader.} \peikai{See also \cite{Bernardeau:2002rev} for a detailed derivation.} We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
+Stating this explicitly could be helpful for a reader.} \peikai{See also \cite{Bernardeau:2002rev} for a detailed derivation of SPT.} We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
 This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
@@
 \eea 
-where we take advantage of the fact that $F_2$ is a symmetric function.\\
-Finally we have:
+where we take advantage of the fact that $F_2$ is a symmetric function. Finally we have:
 \be 
@@
 where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already.
-Also remember to change the survey volume to match DESI and state this.} \peikai{We show the projected error of long-wavelength power spectrum using this quadratic estimator with fiducial value $1$.
+Also remember to change the survey volume to match DESI and state this.} \peikai{In Fig.~\rf{SN}, we show the projected error of long-wavelength power spectrum using this quadratic estimator with fiducial value $1$.
 The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$.
@@
 Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.
-The upper limit of $\vk_s$ was $0.22 \,h\, \rm Mpc^{-1}$.}
+The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}
 

### 2019-10-18 paper/v2.tex
v2

--- 2019-10-17 paper/v1.tex
@@
 \begin{abstract}
-\noindent \peikai{Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them by measuring perturbations on small scales.} \RC{Should really say instead something about  the fact that large scale modes are difficult to measure because they are sensitive to systematic observational  errors in galaxy surveys - not that they can't be measured.} Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
-This arises physically because the growth of small scale structures varies depending on the large scale environment in which they reside.
-This induces small scale clustering in real space and an off-diagonal term in the two-point statistics in Fourier space.
-We can therefore build a quadratic estimator for the large scale field.
-We demonstrate that this quadratic estimator works well with an N-body simulation test \RC{what do we find?
-scales?
-+ final speculative sentence about potential of method to do cosmology}.
-\peikai{We find this quadratic estimator very powerful for reconstructing long-wavelength modes with the $(2.5\,h^{-1}\,\rm Gpc)^3$ simulation.
-It provides us with a novel way of studying large scale structure and topics related.}
+\noindent Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them indirectly by observing their impact on small scales perturbations.
+Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
+This arises physically because small scale structures grow at different rates depending on the large scale environment in which they reside.
+This induces an off-diagonal term in the two-point statistics in Fourier space that we use as the basis for a quadratic estimator for the large scale field.
+We demonstrate that this quadratic estimator works well on an N-body simulation of size  $(2.5\,h^{-1}\,\rm Gpc)^3$.
+In particular, the quadratic estimator successfully reconstructs the long-wavelength modes using only small-scale information.
+This opens up novel opportunities to study structure on the largest observable scales.
 
@@
 \maketitle
-\section{Introduction}
-Measuring the distribution of structures on large scales has been one of the main goals of recent surveys\peikai{, through which we can have a better constraint of $f_{\rm NL}$ or solve large scale anomalies,} despite it is hard to accomplish directly.\RC{Should include brief examples of why it is very interesting - for example to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting} To tackle this problem, relations between long- and short-wavelength modes have been frequently discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
-The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that we can use small scale perturbation to infer large scale information to some extent \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
-In order to fully achieve this goal, we develop in this work a generalized approach of building a quadratic estimator to measure long-wavelength modes indirectly.
-\\
-Starting from second-order standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop}, we can identify the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
-This can be further related to the cosmic microwave background (CMB) lensing case \cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
-Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.\\
+\noindent {\it Introduction.}
+Measuring the distribution of matter on large scales is one of the goals of cosmological surveys.
+The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity.
+%\peikai{, through which we can have a better constraint of $f_{\rm NL}$ or solve large scale anomalies,} despite it is hard to accomplish directly.\RC{Should include brief examples of why it is very interesting - for example to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting}
+Direct measurements are difficult because of systematic effects, so indirect approaches have been considered.
+Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average.
+This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
+The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
+In order to fully achieve this goal, here we construct a quadratic estimator to measure long-wavelength modes indirectly.
+
+Standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop} identifies the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
+Abstractly, this is similar to
+cosmic microwave background (CMB) lensing~\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
+Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.
 The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing.
-The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no-longer zero, due to the effect of large scale modes.
+The same statistical feature shows up in our case as well -- the off-diagonal terms of the small scale correlations are no longer zero, due to the effect of large scale modes.
 Thus we can create a quadratic estimator for long-wavelength modes using exactly the same formalism.
-\\
-We begin with a brief review of SPT up to second-order in section \ref{sec1}.
-We then build the quadratic estimator and compute the detectability of the estimator in section \ref{sec2}.
-In section \ref{sec3} we present a concise study of the estimator with data from N-body simulation.
-Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
-We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014) \cite{Planck:2014cos} cosmological parameters in this work (same as parameters of the N-body simulation).
 
-\section{Standard Perturbation Theory}\label{sec1}
-In this section we review the SPT approach which describes small scale nonlinearity.
+We begin with a brief review of SPT up to second-order, build the quadratic estimator, and then calculate its detectability.
+We then apply the estimator to data from a large N-body simulation and demonstrate that it successfully extracts the large scale modes.
+%Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
+We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014)~\cite{Planck:2014cos} cosmological parameters in this work (to match the parameters of the N-body simulation).
+
+\noindent {\it Standard Perturbation Theory.}\label{sec1}
+%In this section we review the SPT approach which describes small scale nonlinearity.
 \RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter.
@@
 \\
-Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are continuity, Euler and Poisson equations:
+Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are the continuity, Euler and Poisson equations:
 \bea
@@
 (\frac{\partial}{\partial \tau} +\vec{v}(\vec{x},\tau)&\times&\vec{\nabla})\vec{v}(\vec{x},\tau)=-\frac{da}{d\tau}\frac{\vec{v}(\vec{x},\tau)}{a}-\vec{\nabla}\Phi \eql{eulereq}\\
-&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) \eql{fluid3}
+&&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) .\eql{fluid3}
 \eea
-these equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.\\
-We can solve these equations in Fourier space with perturbative expansion \cite{Bernardeau:2002rev}:
+These equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
+We can solve these equations perturbatively in Fourier space~\cite{Bernardeau:2002rev}:
 \bea
@@
 
-\section{Quadratic Estimator}\label{sec2}
+\noindent{\it Quadratic Estimator.}\label{sec2}
 In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}.
@@
 
-\section{Demonstration with an N-Body Simulation}\label{sec3}
+\noindent{\it Demonstration with an N-Body Simulation.}\label{sec3}
 We test the power of the quadratic estimator using data from a cosmological N-body simulation.
@@
 
-\section{Conclusion}\label{sec4}
+\noindent{\it Conclusion.}\label{sec4}
 In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
@@
 
-\acknowledgements
-\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.
-SD, PL and RC are supported by U.S.\ Dept.\ of Energy contract DE-SC0019248.
-SD and RC also acknowledge support from NSF AST-1909193.\\
+%\acknowledgements
+\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
 The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu.

### 2019-10-18 paper/v2.tex
v2

@@
 \eea
-where $D_1$ is the linear growth factor \RC{define this e.g.
+where $D_1$ is the linear growth factor.
+%\RC{define this e.g.
 $\delta(\tau)=D_{1}\delta(0)$} \peikai{defined by $\delta^{(1)}(\vk,\tau)=D_{1}(\tau)\delta_{0}(\vk)$ with $\delta_0$ being the initial density field.
@@
 This equation is already indicated in Eq(4).}.
-The first order term ${\delta}^{(1)}$ corresponds to linear evolution.
-The linear power spectrum is given by this first order term via:
+The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The linear power spectrum is given by this first order term via:
 \be 
@@
 \ee 
-Substituting the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3}, we can solve for the second-order density contrast:
+Substituting the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3} leads to an expression for the second-order density contrast:
 \be
@@
 \be
-F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1})\eql{f2}
+F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}).\eql{f2}
 \ee
@@
 Nonetheless for related calculations in a $\Lambda$CDM universe, the difference is found to be negligible \cite{Takahashi:2008to}, and thus we use the expressions from \ec{pert1} and \ec{f2} throughout this work.\\
-We next compute the two-point correlations of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ \RC{why is this squeezed limit - is $\vk_s,\vk_s' \gg \vk_l$?}\peikai{with $\vk_s,\vk_s' \gg \vk_l$} up to second-order.
-Here $\vk_l$ corresponds to a long-wavelength mode, and $\tau$  is at the present day:
+
+Using this expression for $\delta^{(2)}$, we can calculate the two-point correlation of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ with $\vk_s,\vk_s' \gg \vk_l$.
+Here $\vk_l$ corresponds to a long-wavelength mode, and we suppress the time dependence.
+To second order,
 \bea 
-&& \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{\vk_s+\vk_s'=\vk_l}\vs
-&=&  \langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(2)}(\vec{k}_s') \rangle+\langle {\delta}^{(2)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s') \rangle
+ \langle {\delta}(\vec{k}_s){\delta}(\vec{k}_s') \rangle|_{\vk_s+\vk_s'=\vk_l}&=&
+  \langle {\delta}^{(1)}(\vec{k}_s){\delta}^{(2)}(\vec{k}_s') \rangle\vs
+  &+&\langle {\delta}^{(2)}(\vec{k}_s){\delta}^{(1)}(\vec{k}_s') \rangle.
 \eea 
@@
 \eea 
-\peikai{Need to rephrase (don't know how): We claim that generally correlation function of three Gaussian fields is non-zero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
-\be 
-\langle
-\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
-{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
-\rangle
-=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction}
-\ee 
-$\vk_1$ and $\vk_2$ corresponds to two arbitrary short modes and $\vk_3$ arbitrary long mode.
+%\peikai{Need to rephrase (don't know how): We claim that generally correlation function of three Gaussian fields is non-zero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
+%\be 
+%\langle
+%\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
+%{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
+%\rangle
+%=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction}
+%\ee 
+%$\vk_1$ and $\vk_2$ corresponds to two arbitrary short modes and $\vk_3$ arbitrary long mode.
 The above equation is true since in a real life survey, we can only measure this long-wavelength mode very limited times.
 Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.}\\
-\RC{Maybe this?: The RHS of \ec{integral} includes an integral over the three point correlation function of modes of a Gaussian field.
+When one of the wavenumbers in the 3-point function in \ec{integral} is very small, that mode can be considered as a background mode.
+The small scale modes evolve in the presence of whatever long wavelength modes happen to be present.
+Therefore,
+\bea
+\langle
+%\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
+\delta^{(1)}(\vk_{s}) \delta^{(1)}(\vk_{s}-\vk){\delta^{(1)}}(\vk) 
+\rangle
+&=&\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}-\vk) \rangle {\delta^{(1)}}(\vk)  \vs
+&+&\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk) \rangle {\delta^{(1)}}(\vk_s'-\vk) .
+\vs
+\eql{contraction}
+\eea
+The first term on the right occurs when $\vk$ is small and the second when $\vk_s'-\vk$ is small.
+
+%\RC{Maybe this?: The RHS of \ec{integral} includes an integral over the three point correlation function of modes of a Gaussian field.
 If one of the modes has a much longer wavelength than the others, then its contribution will be limited to a few examples, and a statistical average will not take place.
 In this case, we can move the long wavelength mode outside the bracket, so that the following is a good approximation:
-\be 
-\langle
-\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
-{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
-\rangle
-=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction},
-\ee 
-where $\vk_1$ and $\vk_2$ are two short modes and $\vk_3$ is the long mode.}\\
-We can use this contraction twice in \ec{integral}.
+%\be 
+%\langle
+%\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
+%{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
+%\rangle
+%=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction},
+%\ee 
+%where $\vk_1$ and $\vk_2$ are two short modes and $\vk_3$ is the long mode.}\\
+%We can use this contraction twice in \ec{integral}.
 One use occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, when we can extract ${\delta}^{(1)}(\vk)$; the other is when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\
-Using \ec{lin}, \ec{integral} can be evaluated as:
+Using \ec{lin}, \ec{integral} then becomes:
 \bea 
@@
 \noindent{\it Quadratic Estimator.}\label{sec2}
-In this section we construct the quadratic estimator for long-wavelength modes starting from \ec{2pt}.
-We then forecast the detectability of the quadratic estimator for future surveys.
+We can now construct the quadratic estimator for long-wavelength modes starting from \ec{2pt} and summing over as many pairs as possible with weights that maximize the signal to noise.
 As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
@@
 We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$.
-We discuss the choice of the upper limit later, in section \ref{sec3}.\\
+%We discuss the choice of the upper limit later, in section \ref{sec3}.\\
+
 Assuming Gaussian noise, the projected detectability of a $P(k_l)$ measurement using the quadratic estimator can be expressed as:
@@
 \ee
-where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already.
-Also remember to change the survey volume to match DESI and state this.} \peikai{In Fig.~\rf{SN}, we show the projected error of long-wavelength power spectrum using this quadratic estimator with fiducial value $1$.
+where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
+%\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already. Also remember to change the survey volume to match DESI and state this.} 
+In Fig.~\rf{SN}, we show the projected errors on the long-wavelength power spectrum using this quadratic estimator in a large survey.
 The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$.
-We will see in the next section \ref{sec3} that this choice of the upper limit is very reasonable for our current construction at $z=0$.
-Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$ case).}\\
-\peikai{plot linear or nonlinear? Change ylabel?}
+We will see that this choice of the upper limit is reasonable for our current construction at $z=0$.
+Also notice that $P_{\rm lin}(k_l)$ dominates over $N(k_l)$ in \ec{error} for this upper limit, thus the projected error bars are only slightly wider than the cosmic variance error bars ($N=0$).
+
+%\peikai{plot linear or nonlinear? Change ylabel?}
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
@@
 The cubical box side length of BigMDPL is $2.5\,h^{-1}\,\rm Gpc$.
-We use the dark matter particle data to compute the matter density field, leaving the effect of using galaxies or halos to trace the field \cite{Desjacques:2018rev} to  future work.\\
+We use the dark matter particle data to compute the matter density field, leaving the effect of using galaxies or halos to trace the field \cite{Desjacques:2018rev} to  future work.
+
 We use the code nbodykit \cite{Hand:2018nby} to measure the Fourier density modes, and \ec{quadest} to estimate the long wavelength modes  from the measured short wavelength modes.
-How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$ \peikai{for different values of $\vk_l$}.
+How well the estimator works can be seen from Fig.~\rf{hist}, where we show histograms of the ratio of the estimated mode amplitudes $\hat{\delta}(\vk_l)$ to their true amplitudes $\delta(\vk_l)$ for different values of $\vk_l$.
 The two panels show the differences between a short wavelength mode cutoff of $k_s=0.22\, h\, \rm Mpc^{-1}$ and  $k_s=0.37\,h\, \rm Mpc^{-1}$.
-\peikai{Notice that second-order SPT gets less accurate higher in the nonlinear regime and will produce a bias of our quadratic estimator.
-As we can see in this plot that individual mode amplitudes are basically unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$.
-While for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are more biased (the center of the ratio $\sim 20 \%$ too high) and more incorrect (about $\sim 50 \%$ of the modes have negative real parts of $\delta/\hat{\delta}$) due to the increasing inaccuracy of second-order SPT.
-} \RC{Comment on what the figure shows -  for example individual mode amplitudes are unbiased when $k_s= 0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this here from fig caption: We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are biased (the mode is $\sim 20 \%$ too high) due to the increasing inaccuracy of second-order SPT as we move into nonlinear scales}
+Notice that second-order SPT becomes less accurate as shorter wavelengths are used and will produce a bias of our quadratic estimator.
+The figure shows that individual mode amplitudes are  unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$, while for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are biased (the center of the ratio is $\sim 20 \%$ too high).
+%and more incorrect (about $\sim 50 \%$ of the modes have negative real parts of $\delta/\hat{\delta}$) due to the increasing inaccuracy of second-order SPT.
+}
+%\RC{Comment on what the figure shows -  for example individual mode amplitudes are unbiased when $k_s= 0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this here from fig caption: We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are biased (the mode is $\sim 20 \%$ too high) due to the increasing inaccuracy of second-order SPT as we move into nonlinear scales}
 \Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}

### 2019-10-18 paper/v2.tex
v2

@@
         }
+%\newcommand{\sfigg}[2]{
+%\includegraphics[width=0.424\paperwidth]{../plots/#1}
+%        }
 \newcommand{\sfigg}[2]{
-\includegraphics[width=0.424\paperwidth]{../plots/#1}
+\includegraphics[width=#2]{../plots/#1}
         }
@@
    \begin{figure}[thbp]
-    \sfigg{../plots/#1.pdf}{\columnwidth}
+    \sfigg{../plots/#1.pdf}{.8\paperwidth}
     \caption{{\small #2}}
@@
 \Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
-\\Another goal of this approach is to reproduce large scale structure in real space.
-To test this, we compute real space density fields by taking the inverse transform of both the directly measured long wavelength Fourier modes and the long wavelength modes predicted using the quadratic estimator.
-These density fields, $\delta$ and $\hat{\delta}$ respectively are plotted in Fig.~\rf{real}.
-We can see that \peikai{our quadratic estimator }
-\RC{describe how well it works based on what we can see in the figure}
-\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
-The bottom row shows their difference.
-Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.
-The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}
+
+Another way of examining the success of the quadratic estimator is to transform the estimated density field back to real space to form $\hat\delta(\vec x)$ and then compare with the actual large scale density field $\delta(\vec x)$ in the simulation.
+The 7 panels in the top two rows of Fig.~\rf{real} compare these two fields; each panel is is a slice of the full simulations.
+
+% of this approach is to reproduce large scale structure in real space. 
+%To test this, we compute real space density fields by taking the inverse transform of both the directly measured long wavelength Fourier modes and the long wavelength modes predicted using the quadratic estimator.
+%These density fields, $\delta$ and $\hat{\delta}$ are plotted in . %We can see that \peikai{our quadratic estimator }
+%\RC{describe how well it works based on what we can see in the figure}
+The bottom panel shows the difference between the estimated and true density fields.
+It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.
 
@@
 %\acknowledgements
+\onecolumngrid
+\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
+The bottom row shows their difference.
+Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.
+The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}
+\twocolumngrid
+%\input{main.bbl}
+
 \noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
@@
 
-%\input{main.bbl}
-
 \bibliography{refs}

### 2019-10-21 paper/v2.tex

@@
 In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
-\RC{ State that this is good because we won't be sensitive to observational systematics, sky gradients, dust etc}
-\RC{Give a short list of cool things we can do, with references: measure 3D clustering beyond the matter radiation equality turnover for the first time, look for evidence of general relativistic effects which are strongest on large scales (e.g., \cite{Jeong:2012ls}), look for evidence of large scale anomalies, like in the CMB, constrain non-Gaussianity,  etc }\\
-Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data.
+The estimator works well on an N-Body simulation, so applying this estimator to survey data is an exciting next step.
+Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions, and light-cone effects.
+We do not expect any of these to be show-stoppers, so it is tempting to speculate about the possibilities that will open up with this estimate of the large scale density field.
+First, we can hope to measure 3D clustering on scales larger than the matter radiation equality turnover without worrying about large-scale systematic effects.
+General relativistic effects are strongest on large scales (e.g., \cite{Jeong:2012ls}), and these could be detected.
+There is evidence of large scale anomalies, in the CMB, that could be confronted with maps of large scale structure obtained with this estimator.
+Primordial non-Gaussianity generated by inflation leaves an imprint on the largest scales.
+There is even the possibility of cross-correlating the large-scale matter field with the CMB itself to extract information about the longest wavelength modes in the universe.
+Since the current epoch of acceleration is a large-scale, late-time effect, there is the possibility of learning about the mechanism responsible for acceleration.
+Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory,
+
+%iso ,  etc }\\
+%Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data.
 The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case.
@@
 \\
-Another issue relates to the range of long-wavelength modes that are detectable.
+%Another issue relates to the range of long-wavelength modes that are detectable.
 In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
-Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time.
+%Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time.
 As the length scales are so large, a more realistic situation should deal with observations on the light cone.
@@
 %\acknowledgements
+%\input{main.bbl}
+
+\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
+The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu.
+The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
+
 \onecolumngrid
@@
 \twocolumngrid
-%\input{main.bbl}
-
-\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
-The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu.
-The CosmoSim database (\url{www.cosmosim.org}) providing the file access is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP).
 

### 2019-10-21 paper/v2.tex
minor

@@
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
-We assume a toy survey of boxsize $L=4\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
+We assume a toy survey of boxsize $L=2.5\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
 Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}
@@
 Another way of examining the success of the quadratic estimator is to transform the estimated density field back to real space to form $\hat\delta(\vec x)$ and then compare with the actual large scale density field $\delta(\vec x)$ in the simulation.
-The 7 panels in the top two rows of Fig.~\rf{real} compare these two fields; each panel is is a slice of the full simulations.
+The 7 panels in the top two rows of Fig.~\rf{real} compare these two fields; each panel is a slice of the full simulations.
 

### 2019-10-22 paper/v2.tex
minor

@@
 The estimator works well on an N-Body simulation, so applying this estimator to survey data is an exciting next step.
-Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions, and light-cone effects.
+Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions \cite{Kaiser:1987rsd}, and light-cone effects.
 We do not expect any of these to be show-stoppers, so it is tempting to speculate about the possibilities that will open up with this estimate of the large scale density field.
@@
 \onecolumngrid
-\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
+\Sfigg{real1}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row).
 The bottom row shows their difference.

### 2019-10-22 paper/v2.tex
m

@@
 Since the current epoch of acceleration is a large-scale, late-time effect, there is the possibility of learning about the mechanism responsible for acceleration.
-Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory,
+Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory.
 

### 2019-10-22 paper/v2.tex
minor
1

@@
 cosmic microwave background (CMB) lensing~\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
-Similarly in our case the short-wavelength mode's nonlinear terms are related its large scale environment.
+Similarly in our case the short-wavelength mode's nonlinear terms are related to its large scale environment.
 The construction of a CMB lensing quadratic estimator makes use of the fact that small scale two-point correlations of CMB temperature modes have off-diagonal terms due to large scale perturbations caused by gravitational lensing.
@@
 Another way of examining the success of the quadratic estimator is to transform the estimated density field back to real space to form $\hat\delta(\vec x)$ and then compare with the actual large scale density field $\delta(\vec x)$ in the simulation.
-The 7 panels in the top two rows of Fig.~\rf{real} compare these two fields; each panel is a slice of the full simulations.
+The 7 panels in the top two rows of Fig.~\rf{real1} compare these two fields; each panel is a slice of the full simulations.
 

### 2019-10-22 paper/v2.tex
1

@@
 The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity.
-%\peikai{, through which we can have a better constraint of $f_{\rm NL}$ or solve large scale anomalies,} despite it is hard to accomplish directly.\RC{Should include brief examples of why it is very interesting - for example to constrain fNL, large scale anomalies, detect matter radiation-equality turnover - make it clear that a measurement would be exciting}
 Direct measurements are difficult because of systematic effects, so indirect approaches have been considered.
@@
 We then apply the estimator to data from a large N-body simulation and demonstrate that it successfully extracts the large scale modes.
-%Finally we conclude this work and discuss future work related to this in section \ref{sec4}.
-We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014)~\cite{Planck:2014cos} cosmological parameters in this work (to match the parameters of the N-body simulation).
+We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014)~\cite{Planck:2014cos} cosmological parameters in this work (to match the parameters of the N-body simulation).\\
 
 \noindent {\it Standard Perturbation Theory.}\label{sec1}
-%In this section we review the SPT approach which describes small scale nonlinearity.
-\RC{Say something about: see also a textbook, or the Bernardeau review reference - it looks to me that some of your notation is from the latter.
-Stating this explicitly could be helpful for a reader.} \peikai{See also \cite{Bernardeau:2002rev} for a detailed derivation of SPT.} We then compute the off-diagonal term of two short-wavelength modes in the squeezed limit.
-This non-zero off-diagonal term proportional to a long-wavelength mode will be the key factor of constructing the quadratic estimator.
-\\
 Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are the continuity, Euler and Poisson equations:
@@
 where $D_1$ is the linear growth factor. 
-%\RC{define this e.g.
-$\delta(\tau)=D_{1}\delta(0)$} \peikai{defined by $\delta^{(1)}(\vk,\tau)=D_{1}(\tau)\delta_{0}(\vk)$ with $\delta_0$ being the initial density field.
-Is it necessary?
-This equation is already indicated in Eq(4).}.
 The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The linear power spectrum is given by this first order term via:
@@
 \eea 
-%\peikai{Need to rephrase (don't know how): We claim that generally correlation function of three Gaussian fields is non-zero under following consideration: if a three-point correlation function consists of two short-wavelength modes and one long-wavelength mode, we can do the following contraction:
-%\be 
-%\langle
-%\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
-%{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
-%\rangle
-%=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction}
-%\ee 
-%$\vk_1$ and $\vk_2$ corresponds to two arbitrary short modes and $\vk_3$ arbitrary long mode.
-The above equation is true since in a real life survey, we can only measure this long-wavelength mode very limited times.
-Thus it won't have any statistical property and we can safely extract the long-wavelength mode out of the bracket.}\\
 When one of the wavenumbers in the 3-point function in \ec{integral} is very small, that mode can be considered as a background mode.
@@
 \langle
-%\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
 \delta^{(1)}(\vk_{s}) \delta^{(1)}(\vk_{s}-\vk){\delta^{(1)}}(\vk) 
@@
 The first term on the right occurs when $\vk$ is small and the second when $\vk_s'-\vk$ is small.
-
-%\RC{Maybe this?: The RHS of \ec{integral} includes an integral over the three point correlation function of modes of a Gaussian field.
-If one of the modes has a much longer wavelength than the others, then its contribution will be limited to a few examples, and a statistical average will not take place.
-In this case, we can move the long wavelength mode outside the bracket, so that the following is a good approximation:
-%\be 
-%\langle
-%\contraction{}{{\delta}}{{\delta^{(1)}\;\;\;\;}(}{}
-%{\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}){\delta^{(1)}}(\vk_3) 
-%\rangle
-%=\langle {\delta^{(1)}}(\vk_{1}) {\delta^{(1)}}(\vk_{2}) \rangle {\delta^{(1)}}(\vk_3)  \eql{contraction},
-%\ee 
-%where $\vk_1$ and $\vk_2$ are two short modes and $\vk_3$ is the long mode.}\\
-%We can use this contraction twice in \ec{integral}.
-One use occurs when $|\vk| \ll |\vk_s|,\, |\vk_s'-\vk|$, when we can extract ${\delta}^{(1)}(\vk)$; the other is when $|\vk_s'-\vk| \ll |\vk|,\,|\vk_s|$.\\
 Using \ec{lin}, \ec{integral} then becomes:
@@
 \eea 
-\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.
+\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.\\
 
@@
 We find by testing that the value of $N$ is very insensitive to the choice of the lower limit of the integration \ec{a}, since most of the contribution comes from large $k_s$.
-%We discuss the choice of the upper limit later, in section \ref{sec3}.\\
 
@@
 where $V$ is the volume of a survey and we compute the detectability for a set of narrow $k_l$-bins each separated by width $\Delta k$.
-%\RC{ Write a couple of sentences about Figure 1, bearing in mind that you have put information in the caption already. Also remember to change the survey volume to match DESI and state this.} 
 In Fig.~\rf{SN}, we show the projected errors on the long-wavelength power spectrum using this quadratic estimator in a large survey.
@@
 
-%\peikai{plot linear or nonlinear? Change ylabel?}
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
@@
 The figure shows that individual mode amplitudes are  unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$, while for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are biased (the center of the ratio is $\sim 20 \%$ too high).
-%and more incorrect (about $\sim 50 \%$ of the modes have negative real parts of $\delta/\hat{\delta}$) due to the increasing inaccuracy of second-order SPT.
-}
-%\RC{Comment on what the figure shows -  for example individual mode amplitudes are unbiased when $k_s= 0.15 \rm Mpc^{1}$, and predicted to within $\sim x \%$} \RC{moved this here from fig caption: We can see that the results for $k_s=0.25 \rm Mpc^{1}$ are biased (the mode is $\sim 20 \%$ too high) due to the increasing inaccuracy of second-order SPT as we move into nonlinear scales}
 \Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
@@
 
-% of this approach is to reproduce large scale structure in real space. 
-%To test this, we compute real space density fields by taking the inverse transform of both the directly measured long wavelength Fourier modes and the long wavelength modes predicted using the quadratic estimator.
-%These density fields, $\delta$ and $\hat{\delta}$ are plotted in . %We can see that \peikai{our quadratic estimator }
-%\RC{describe how well it works based on what we can see in the figure}
 The bottom panel shows the difference between the estimated and true density fields.
-It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.
+It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.\\
 
@@
 Since the current epoch of acceleration is a large-scale, late-time effect, there is the possibility of learning about the mechanism responsible for acceleration.
-Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory.
-
-%iso ,  etc }\\
-%Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data.
-The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case.
-Thus, to detect even larger scales, we may need to use contributions from higher order perturbations and expand the integration range to reduce the noise level.
-\\
-%Another issue relates to the range of long-wavelength modes that are detectable.
-In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\
-%Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time.
-As the length scales are so large, a more realistic situation should deal with observations on the light cone.
-The expression for the quadratic estimator to be generalized to take this into account.
-Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information.
-Finally, when applied to datasets consisting of halos or galaxies, the approach should be modified to include galaxy bias.
-We also leave this to future work.\\
-
-%\acknowledgements
-%\input{main.bbl}
+Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory.\\
 

### 2019-10-22 paper/v2.tex
1
minor
v. minor

@@
 \begin{abstract}
-\noindent Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them indirectly by observing their impact on small scales perturbations.
+\noindent Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them indirectly by observing their impact on small scale perturbations.
 Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
@@
 The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity.
-Direct measurements are difficult because of systematic effects, so indirect approaches have been considered.
+Direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered.
 Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average.
@@
 \be 
-\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
+\langle \hat{\delta}^{(1)}(\vk_{l})\hat{\delta}^{(1)*}(\vk_{l}') \rangle = (2\pi)^3 \delta_{\rm D}(\vk_{l}-\vk_{l}')[P_{\rm lin}(k_{l})+N(\vk_l)]
 \ee 
@@
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
-We assume a toy survey of boxsize $L=2.5\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
+We assume a toy survey of boxsize $L=2.5\, h^{-1}\rm\, Gpc$, \RC{Should we refer to DESI directly?} thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
 Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}
@@
 The 7 panels in the top two rows of Fig.~\rf{real1} compare these two fields; each panel is a slice of the full simulations.
-
 The bottom panel shows the difference between the estimated and true density fields.

### 2019-10-24 paper/v2.tex
minor

@@
 We then apply the estimator to data from a large N-body simulation and demonstrate that it successfully extracts the large scale modes.
-We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014)~\cite{Planck:2014cos} cosmological parameters in this work (to match the parameters of the N-body simulation).\\
+We use a flat $\Lambda$CDM model with Planck Collaboration XVI (2014)~\cite{Planck:2014cos} cosmological parameters in this work (to match the parameters of the N-body simulation).
 
@@
 Note that \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in an Einstein-de Sitter universe.
-Nonetheless for related calculations in a $\Lambda$CDM universe, the difference is found to be negligible \cite{Takahashi:2008to}, and thus we use the expressions from \ec{pert1} and \ec{f2} throughout this work.\\
-
+Nonetheless for related calculations in a $\Lambda$CDM universe, the difference is found to be negligible \cite{Takahashi:2008to}, and thus we use the expressions from \ec{pert1} and \ec{f2} throughout this work.
 Using this expression for $\delta^{(2)}$, we can calculate the two-point correlation of two short-wavelength modes $\vk_s$ and $\vk_s'$, in the squeezed limit $\vk_l=\vk_s+\vk_s'$ with $\vk_s,\vk_s' \gg \vk_l$.
@@
 \eea 
-\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.\\
+\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.
 
@@
 \Sfig{SN}{Long-wavelength power spectrum and its error from \ec{error} which can be expressed as $P(k_l)\sigma(k_l)$.
-We assume a toy survey of boxsize $L=2.5\, h^{-1}\rm\, Gpc$, \RC{Should we refer to DESI directly?} thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
+We assume a toy survey of boxsize $L=2.5\, h^{-1}\rm\, Gpc$, thus volume $V=L^3$ and width $\Delta k = 2\pi/L$.
 Moreover, we set the integration range for $\vk_s$ from $0.03 \,h \,\rm Mpc^{-1}$ to $0.22\,h\,\rm Mpc^{-1}$.}
@@
 The bottom panel shows the difference between the estimated and true density fields.
-It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.\\
-
+It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.
 \noindent{\it Conclusion.}\label{sec4}

### 2019-10-24 paper/v2.tex
1

@@
 \affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
 \author{\large Scott Dodelson}
 \affiliation{Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+\affiliation{McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
 \author{\large Rupert A. C. Croft}
@@
 Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average.
-This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Barreira:2017res}.
+This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Li:2014ssc}\cite{Barreira:2017res}.
 The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
@@
 Abstractly, this is similar to
-cosmic microwave background (CMB) lensing~\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
+cosmic microwave background (CMB) lensing~\cite{Hu:2001dt}\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
 Similarly in our case the short-wavelength mode's nonlinear terms are related to its large scale environment.

### 2020-02-08 paper/v2.tex
1

@@
 \noindent {\it Introduction.}
-Measuring the distribution of matter on large scales is one of the goals of cosmological surveys.
+Measuring the distribution of matter on large scales is one of the goals of cosmological surveys \cite{LSST:2012ls}\cite{Wfirst:2012jg}.
 The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity.
@@
 Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average.
-This relation between long- and short-wavelength modes has been discussed in recent years \cite{Baldauf:2011fer}\cite{Li:2014ssc}\cite{Barreira:2017res}.
+This relation between long- and short-wavelength modes has been discussed in recent years \cite{Masui:2010prim}\cite{Baldauf:2011fer}\cite{Jeong:2012foss}\cite{Li:2014ssc}\cite{Zhu:2016tidal}\cite{Barreira:2017res}\cite{Zhu:2018cm}.
 The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
@@
 \bea
-\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\times [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0\eql{fluid1} \\
-(\frac{\partial}{\partial \tau} +\vec{v}(\vec{x},\tau)&\times&\vec{\nabla})\vec{v}(\vec{x},\tau)=-\frac{da}{d\tau}\frac{\vec{v}(\vec{x},\tau)}{a}-\vec{\nabla}\Phi \eql{eulereq}\\
+\frac{\partial \delta(\vec{x},\tau)}{\partial \tau} &+&\vec{\nabla}\cdot [(1+\delta(\vec{x},\tau))\vec{v}(\vec{x},\tau)] =0\eql{fluid1} \\
+\bigg[\frac{\partial}{\partial \tau} +\vec{v}(\vec{x},\tau)\cdot&\vec{\nabla}& \bigg]\vec{v}(\vec{x},\tau)=-\frac{da}{d\tau}\frac{\vec{v}(\vec{x},\tau)}{a}-\vec{\nabla}\Phi \eql{eulereq}\\
 &&\nabla^2 \Phi = 4\pi G a^2 \bar{\rho}_{\rm m} \delta(\vec{x},\tau) .\eql{fluid3}
 \eea
-These equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
+\peikai{Here $a$ is the cosmological scale factor, $\Phi$ is the 3D gravitational potential and $\bar{\rho}_{\rm m}(a)$ is the mean matter density.} These equations fully determine the time evolution of the local density contrast $\delta$ and the peculiar velocity field $\vec{v}=d\vec{x}/d\tau$.
 We can solve these equations perturbatively in Fourier space~\cite{Bernardeau:2002rev}:
@@
 where $D_1$ is the linear growth factor. 
-The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The linear power spectrum is given by this first order term via:
+The first order term ${\delta}^{(1)}$ corresponds to linear evolution. The linear power spectrum is given by this first order term via \peikai{averaging over modes in Fourier space}:
 \be 
@@
 \ee 
-Substituting the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3} leads to an expression for the second-order density contrast:
+\peikai{Here $\delta_{\rm D}$ is the Dirac delta function.} Substituting the perturbative series \ec{pert1} and \ec{pert2} into the Fourier transformed fluid equations \ec{fluid1}-\ec{fluid3} leads to an expression for the second-order density contrast:
 \be
@@
 \be
-F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}(\frac{k_1}{k_2}+\frac{k_2}{k_1}).\eql{f2}
+F_{2}(\vk_1,\vk_2)=\frac{5}{7}+\frac{2}{7}\frac{(\vk_1\cdot \vk_2)^2}{k_1^2 k_2^2}+\frac{\vk_1\cdot \vk_2}{2k_1k_2}\bigg[\frac{k_1}{k_2}+\frac{k_2}{k_1}\bigg].\eql{f2}
 \ee
-Note that \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in an Einstein-de Sitter universe.
+Note that \ec{pert1}, \ec{pert2} and \ec{f2} are completely accurate only in an Einstein-de Sitter universe \peikai{and also assuming the case of a pressureless perfect fluid}.
 Nonetheless for related calculations in a $\Lambda$CDM universe, the difference is found to be negligible \cite{Takahashi:2008to}, and thus we use the expressions from \ec{pert1} and \ec{f2} throughout this work.
@@
 The small scale modes evolve in the presence of whatever long wavelength modes happen to be present.
-Therefore,
+Therefore,  \peikai{we can take the long-wavelength mode out of the bracket:}
 \bea
 \langle
-\delta^{(1)}(\vk_{s}) \delta^{(1)}(\vk_{s}-\vk){\delta^{(1)}}(\vk) 
+\delta^{(1)}(\vk_{s}) \delta^{(1)}(\vk_{s}'-\vk){\delta^{(1)}}(\vk) 
 \rangle
-&=&\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}-\vk) \rangle {\delta^{(1)}}(\vk)  \vs
+&=&\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk_{s}'-\vk) \rangle {\delta^{(1)}}(\vk)  \vs
 &+&\langle {\delta^{(1)}}(\vk_{s}) {\delta^{(1)}}(\vk) \rangle {\delta^{(1)}}(\vk_s'-\vk) .
@@
 \end{eqnarray} 
-with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$  defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
+with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ \peikai{is the normalization factor} defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-g(\vec{k}_{s},\vec{k}_{s}')=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}
+g(\vec{k}_{s},\vec{k}_{s}')
+&=&\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs
+&=&\frac{F_2(-\vec{k}_s,\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s)+F_2(-\vec{k}_s',\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s')}{P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs 
 \end{eqnarray} 

### 2020-02-12 paper/v2.tex
minor

@@
 \includegraphics[width=#2]{../plots/#1}
+        }
+\newcommand{\sfiggg}[2]{
+\includegraphics[width=0.4\paperwidth]{../plots/#1}
         }
@@
 \begin{abstract}
-\noindent Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys but we can study them indirectly by observing their impact on small scale perturbations.
+\noindent Large scale density modes are difficult to measure because they are sensitive to systematic observational errors in galaxy surveys, but we can study them indirectly by observing their impact on small scale perturbations.
 Cosmological perturbation theory predicts that second-order density inhomogeneities are a convolution of a short- and a long-wavelength mode.
@@
 \maketitle
-\noindent {\it Introduction.}
+\section{Introduction}
 Measuring the distribution of matter on large scales is one of the goals of cosmological surveys \cite{LSST:2012ls}\cite{Wfirst:2012jg}.
@@
 Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average.
-This relation between long- and short-wavelength modes has been discussed in recent years \cite{Masui:2010prim}\cite{Baldauf:2011fer}\cite{Jeong:2012foss}\cite{Li:2014ssc}\cite{Zhu:2016tidal}\cite{Barreira:2017res}\cite{Zhu:2018cm}.
+This relation between long- and short-wavelength modes has been discussed in recent years \cite{Masui:2010prim}\cite{Baldauf:2011fer}\cite{Jeong:2012foss}\cite{Jasche:2013bay}\cite{Leclercq:2013remp}\cite{Li:2014ssc}\cite{Zhu:2016tidal}\cite{Barreira:2017res}\cite{Seljak:2017opt}\cite{Akitsu:2018dist}\cite{Foreman:2018line}\cite{Zhu:2018cm}.
 The method of using the small scale position-dependent power spectrum to compute the squeezed-limit bispectrum also indicates that small scale perturbations can be used to infer large scale information \cite{Chiang:2014pos}\cite{Chiang:2015poss}.
@@
 
-Standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop} identifies the second-order perturbation of a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
+Standard perturbation theory (SPT) \cite{Goroff:1986sts}\cite{Makino:1992fs}\cite{Jain:1994sop} identifies the second-order contribution to a short-wavelength mode as a convolution of a short- and a long-wavelength mode.
 Abstractly, this is similar to
-cosmic microwave background (CMB) lensing~\cite{Hu:2001dt}\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along line of sight.
+cosmic microwave background (CMB) lensing~\cite{Hu:2001dt}\cite{Hu:2002mr}, where the CMB temperature field has a second-order correction due to the gravitational field along the line of sight.
 Similarly in our case the short-wavelength mode's nonlinear terms are related to its large scale environment.
@@
 
-We begin with a brief review of SPT up to second-order, build the quadratic estimator, and then calculate its detectability.
+We begin with a brief review of SPT up to second-order, build the quadratic estimator, and then assess its detectability.
 We then apply the estimator to data from a large N-body simulation and demonstrate that it successfully extracts the large scale modes.
@@
 
-\noindent {\it Standard Perturbation Theory.}\label{sec1}
+\section{Standard Perturbation Theory}\label{sec1}
 Starting from a perfect pressureless fluid, the nonrelativistic cosmological fluid equations are the continuity, Euler and Poisson equations:
@@
 \eea
-The first term on the right occurs when $\vk$ is small and the second when $\vk_s'-\vk$ is small.
+\Sfig{LWM}{\peikai{\ec{contraction} occurs when $\vec{k}\ll\vec{k}_s,\vec{k}'_s$ or $\vec{k}'_s-\vec{k}\ll\vec{k}_s,\vec{k}'_s$, which corresponds to the two terms shown in this figure.}}
+\peikai{Delete: The first term on the right occurs when $\vk$ is small and the second when $\vk_s'-\vk$ is small.}
 Using \ec{lin}, \ec{integral} then becomes:
@@
 \eea 
-\ec{2pt} suggests that we can estimate long-wavelength modes using short-wavelength modes.
+This suggests that we can estimate long-wavelength modes using short-wavelength modes.
+\peikai{Since the left-hand side of \ec{2pt} has only short modes while the right-hand side of it is sensitive to long modes.}
 
 \noindent{\it Quadratic Estimator.}\label{sec2}
-We can now construct the quadratic estimator for long-wavelength modes starting from \ec{2pt} and summing over as many pairs as possible with weights that maximize the signal to noise.
+We can now construct the quadratic estimator for long-wavelength modes starting from \ec{2pt} and summing over as many pairs as possible with weights that maximize the signal-to-noise.
 As with the case of CMB lensing, we can write the general form of the estimator by averaging over pairs of short-wavelength modes:
@@
 \end{eqnarray} 
-with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ \peikai{is the normalization factor} defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
+with $g$ being a weighting function, $\vk_s'=\vk_l-\vk_s$ and $A$ \peikai{is the normalization prefactor} defined by requiring that $\langle \hat{\delta}^{(1)}(\vec{k}_l) \rangle={\delta}^{(1)}(\vec{k}_l)$:
 \begin{eqnarray}
@@
 \begin{eqnarray}
-g(\vec{k}_{s},\vec{k}_{s}')
-&=&\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs
+&&g(\vec{k}_{s},\vec{k}_{s}')
+=\frac{f(\vec{k}_{s},\vec{k}_{s}')}{2P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs
 &=&\frac{F_2(-\vec{k}_s,\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s)+F_2(-\vec{k}_s',\vec{k}_s+\vec{k}_s')P_{\rm lin}(k_s')}{P_{\rm nl}(k_{s})P_{\rm nl}(k_{s}')}\vs 
@@
 
-\noindent{\it Demonstration with an N-Body Simulation.}\label{sec3}
+\section{Demonstration with an N-Body Simulation}\label{sec3}
 We test the power of the quadratic estimator using data from a cosmological N-body simulation.
@@
 Notice that second-order SPT becomes less accurate as shorter wavelengths are used and will produce a bias of our quadratic estimator.
-The figure shows that individual mode amplitudes are  unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$, while for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are biased (the center of the ratio is $\sim 20 \%$ too high).
-\Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges.}
+The figure shows that individual mode amplitudes are  unbiased when $k_{s,\rm max}= 0.22\,h\, \rm Mpc^{-1}$, while for $k_{s,\rm max}=0.37\,h\, \rm Mpc^{-1}$, the results are biased (the center of the ratio is $\sim 20 \%$ too high\peikai{, and the histogram of the polar angle of $\hat{\delta}(\vk_l)/\delta(\vk_l)$ is less peaked at $0$.}).
+\Sfig{hist}{Comparison of measured and predicted Fourier mode amplitudes: histograms of number counts of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$ for two different $k_s$ integration ranges\peikai{, $x$-axis shows the magnitude of $|\hat{\delta}(\vk_l)/\delta(\vk_l)|$.}}
 
@@
 It is apparent that the differences are much smaller than the overdensities; equivalently the estimator does an excellent job of extracting the large scale density field.
-\noindent{\it Conclusion.}\label{sec4}
+\section{Conclusion}\label{sec4}
 In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
-The estimator works well on an N-Body simulation, so applying this estimator to survey data is an exciting next step.
+The estimator works well on an N-Body simulation, so applying this estimator to survey data is \peikai{the logical} next step.
 Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions \cite{Kaiser:1987rsd}, and light-cone effects.
 We do not expect any of these to be show-stoppers, so it is tempting to speculate about the possibilities that will open up with this estimate of the large scale density field.
-First, we can hope to measure 3D clustering on scales larger than the matter radiation equality turnover without worrying about large-scale systematic effects.
+First, we can hope to measure 3D clustering on scales larger than the scale entering the horizon at matter-radiation equality without worrying about large-scale systematic effects.
 General relativistic effects are strongest on large scales (e.g., \cite{Jeong:2012ls}), and these could be detected.
@@
 Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory.\\
-
-\noindent We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
+\acknowledgements
+We thank Adam Solomon, Duncan Campbell, Fabian Schmidt and Lam Hui for resourceful discussions.  This work is supported by U.S.\ Dept.\ of Energy contract DE-SC0019248 and NSF AST-1909193.
 The BigMDPL simulation was performed at LRZ Munich within the PRACE project pr86bu.

### 2020-02-12 paper/response.tex
response

\documentclass{article}
\usepackage[utf8]{inputenc}
\newcommand\sd[1]{\emph{\bf [SD: #1]}}

\title{Response}
\author{Peikai Li, Scott Dodelson and Rupert A. C. Croft}
\date{}
\begin{document}

\maketitle
\noindent We sincerely thank the referees for their helpful comments and suggestions, which have significantly improved the manuscript.\\ \\
Following are the specific changes we have made:\\ \\
---------------------------------------------------------------------\\
Report of Referee A -- LK17288/Li\\
---------------------------------------------------------------------\\
\begin{itemize}
\item Referee's suggestion: \textbf{Although the paper shows solid analysis and demonstration with N-body
simulation and the method is relatively new, the small-scale
reconstruction has appeared in Physical Reviews in a couple of times:
for measuring gravitational waves (Masui \& Pen 2010, Jeong \&
Kamionkowski 2011, both PRL), for reconstructing the missing
long-wavelength mode for the 21cm surveys (Zhu, Pen+2015; 2016, both
PRD). All of the references mentioned above are missing in the paper.} \\ \\
Response: We cited all these papers.
\item Referee's suggestion: \textbf{In eq. (1)-(2), the authors use rather unconventional notation
$\times$ to represent the scalar product of two vectors.}
\\ \\Response: We fixed this error. 
\item Referee's suggestion: \textbf{Although the authors mention the 20\% bias on the right panel of Fig
2, showing summary statistics for the figure might be more helpful for
readers to understand the result.}
\\ \\Response: We also stated that the behavior of polar angle difference of the estimated and directly measured modes is worse in the second case. 
\item \textbf{There is a missing reference (shown as ??) on page 3.}\\ \\
Response: We fixed this error.\\

\end{itemize} 
---------------------------------------------------------------------\\
Report of Referee B -- LK17288/Li\\
---------------------------------------------------------------------\\

\begin{itemize}
\item Referee's suggestion: \textbf{First sentence is too long—split}
\\ \\Response: This is similar to the comment from Referee A; please see our response there.
\item Referee's suggestion: \textbf{\\Should have citations for upcoming surveys;\\ Overall I think much more connection to the literature on density reconstruction needs to be made. e.g. work by Jens Jasche, work by Uros Seljak, Florent Leclercq, etc. \\}
\\ \\Response: Cited LSST and WFIRST as upcoming surveys and the papers referee has recommended.
\item Referee's suggestion: \textbf{\\1. An large-scale -$>$ a large-scale;\\2. Second-order perturbation of -$>$ contribution to; \\3. Along line of sight -$>$ missing the; \\4. Calculate its detectability -$>$ assess; \\ 5. Large parens in equation 2 around lhs; \\ 6. Need to define everything in (1)-(3): missing Phi, rho\_m, a, tau; \\7. define the Dirac delta distribution in the text
Also define what $<>$ means;\\ 8. Large parens in equation 8 last term;\\ 9. Say in words what you have done in equation 11—take the low-k mode outside the
expectation value; \\
10. I think the little f function is necessary, just combine (13) and (14); \\ 11. Below (14), explain more: you mean that the lhs of (13) has only short modes, but the
rhs shows sensitivity to long modes; \\ 12. Signal-to-noise needs dashes;\\ 13. In equation (19), if you would not have used the f function, you would find that the factor of 2 cancels out. And the weight is more understandable written as
$[F2*P_{lin}(ks) + F2*P_{lin}(ks’)]/P_{nl}*P_{nl}]$ because it’s basically dividing out nonlinearities
and then rescaling by a particular estimate of the nonlinearity;\\ 14. Bottom left page 3: Fig ?? Missing number in text;\\ 15. formatting at top of page 3 is not good; 16. “Larger than the matter radiation equality”—missing dash. Clearer would be “than the scale entering the horizon at matter-radiation equality”; \\17. Fig 2 caption is not ideal—please actually state what this Figure shows in the caption; \\18. An exciting next step”—that seems subjective. I think you should just say “is the logical next step”.}
\\ \\Response: We have improved these expressions according to the suggestions here.
\item Referee's suggestion: \textbf{Dash in Fourier-transformed}
\\ \\Response: We don't think it is necessary in our case. First of all, we don't think it will cause much confusion. Secondly, the definition of the quadratic estimator ( Eq(15) ) already had a hat on it. We feel that it will be redundant for it to have both "hat" and "dash".
\item Referee's suggestion: \textbf{“Completely accurate” is misleading: even in that case, you’ve assumed a perfect fluid,
whereas in reality we think CDM satisfies the collision less Boltzmann equation.}
\\ \\Response: We stated that we also assumed the case of a pressureless perfect fluid.
\item Referee's suggestion: \textbf{I think the little f function is necessary, just combine (13) and (14).}
\\ \\Response: We think it will be more clear not to combine these two equations.
\\ \\Response: We stated that we also assumed the case of a pressureless perfect fluid.
\item Referee's suggestion: \textbf{isn’t A just basically normalizing the weights so that they integrate to unity?
Why not state that, it’s more physical.}
\\ \\Response: We stated that A is a normalization prefactor.
\item Referee's suggestion: \textbf{I suspect halos will make this worse. Basically you don’t account for biasing, but if the
biasing is not trivial then the optimal estimator is wrong.}
\\ \\Response: In our second paper, we will show that we can still get a good estimate with halo bias considered.
\\ \\

\textbf{Questions that I can't answer...}
\item As one of the applications, the authors mention the primordial
non-Gaussianity. The referee believes that primordial non-Gaussianity
deserves special attention here because its presence can potentially
change the estimator completely (by changing the nature of the
long-short correlation).
\item Also, there has been the idea of directly measuring large-scale modes using IM and then delensing—that should be cited.
\item \textbf{not sure if these two needs to be answered.} Is there a way to use kSZ velocities in concert with this? They offer constrains on large modes too an d wonder if there’s an optimal combination of them with short density modes.\\ \\ We do not expect any of these to be show-stoppers . . .” is just state with no justification. RSD really remove small-scale information from the field. Also not mentioned at all was baryonic effects, which Chisari + 2016 shows can change P(k) at k$\sim$0.4 by 5\%. If small scale info is being used optimally where the optimal weight just comes from the F2 kernel, well, this kernel does not include baryon physics, so these weights are no longer optimal in the presence of baryons. \textbf{We don't use modes up to k $\sim$ 0.4, isn't that right? But I'm not sure about the effect RSD would have.}
\item Why would confronting large-scale CMB anomalies with LSS help? Perhaps should be clarified. 
\item I think also adding forecasts of how much this reconstruction could improve relevant cosmological parameters would be good. “Successfully reconstructs” is subjective; quantifying how much additional information you get on X or Y cosmological parameter would be objective, and hence better.

\end{itemize}

\end{document}

### 2020-02-20 paper/response.tex
1

@@
 \usepackage[utf8]{inputenc}
+\usepackage{hyperref}
 \newcommand\sd[1]{\emph{\bf [SD: #1]}}
@@
 Response: We fixed this error.\\
+\item \textbf{As one of the applications, the authors mention the primordial
+non-Gaussianity. The referee believes that primordial non-Gaussianity
+deserves special attention here because its presence can potentially
+change the estimator completely (by changing the nature of the
+long-short correlation)}\\ \\
+Response:  We agree that primordial non-Gaussianity can change the nature of the long-short correlations, and so could be constrained by comparing the indirectly inferred modes with directly measured large-scale modes, on scales where this can be done, (modulo the usual observational effects).\\
 
@@
 \\ \\Response: In our second paper, we will show that we can still get a good estimate with halo bias considered.
-\\ \\
-
-\textbf{Questions that I can't answer...}
-\item As one of the applications, the authors mention the primordial
-non-Gaussianity. The referee believes that primordial non-Gaussianity
-deserves special attention here because its presence can potentially
-change the estimator completely (by changing the nature of the
-long-short correlation).
-\item Also, there has been the idea of directly measuring large-scale modes using IM and then delensing—that should be cited.
-\item \textbf{not sure if these two needs to be answered.} Is there a way to use kSZ velocities in concert with this?
-They offer constrains on large modes too an d wonder if there’s an optimal combination of them with short density modes.\\ \\ We do not expect any of these to be show-stoppers .
-.
-.” is just state with no justification.
+\item Referee's suggestion: \textbf{Also, there has been the idea of directly measuring large-scale modes using IM and then delensing—that should be cited.}
+\\ \\Response: We cited \url{https://arxiv.org/pdf/1908.08128.pdf}.
+\item Referee's suggestion: \textbf{Is there a way to use kSZ velocities in concert with this?
+They offer constrains on large modes too an d wonder if there’s an optimal combination of them with short density modes.}
+\\ \\Response: We agree that these could be another tracer of large-scale modes and it would be good for us to compare what we get from both methods.
+We cited a relevant paper \url{https://ui.adsabs.harvard.edu/abs/2009PhRvD..80f2003K/abstract}
+\item Referee's suggestion: \textbf{We do not expect any of these to be show-stoppers ...” is just state with no justification.
 RSD really remove small-scale information from the field.
 Also not mentioned at all was baryonic effects, which Chisari + 2016 shows can change P(k) at k$\sim$0.4 by 5\%.
-If small scale info is being used optimally where the optimal weight just comes from the F2 kernel, well, this kernel does not include baryon physics, so these weights are no longer optimal in the presence of baryons.
-\textbf{We don't use modes up to k $\sim$ 0.4, isn't that right?
-But I'm not sure about the effect RSD would have.}
-\item Why would confronting large-scale CMB anomalies with LSS help? Perhaps should be clarified. 
-\item I think also adding forecasts of how much this reconstruction could improve relevant cosmological parameters would be good.
-“Successfully reconstructs” is subjective; quantifying how much additional information you get on X or Y cosmological parameter would be objective, and hence better.
+If small scale info is being used optimally where the optimal weight just comes from the F2 kernel, well, this kernel does not include baryon physics, so these weights are no longer optimal in the presence of baryons.}
+\\ \\Response: We don't think we need to consider baryonic effects at current stage because we only used $k$ modes up to $0.22 \, h \,\rm Mpc^{-1}$.
+We will consider RSD and potentially baryonic effects in our next work, when we apply this method to a light cone.
+\item Referee's suggestion: \textbf{Why would confronting large-scale CMB anomalies with LSS help? Perhaps should be clarified.}
+\\ \\Response: We clarified (in the paper) as follows: One physical mechanism that has been proposed as a possible explanation for the deficit in the large-angle CMBtemperature correlations is a suppression of primordial power on ~ Gpc scales.
+It would be very useful to verify if this new physics is also present in other probes of large-scale structure"  We also cited \url{https://ui.adsabs.harvard.edu/abs/2011JCAP...10..012H/abstract} in support of this.
+\item Referee's suggestion: \textbf{I think also adding forecasts of how much this reconstruction could improve relevant cosmological parameters would be good.
+“Successfully reconstructs” is subjective; quantifying how much additional information you get on X or Y cosmological parameter would be objective, and hence better.}
+\\ \\Response: We prefer to compute forecasts for cosmological parameters using our future work, which will include more realism, such as light cone effects, galaxy bias and redshift distortions, and it would be premature to do it here.
+We also included a quantitative comment that the current largest scale published measurement of the three dimensional power spectrum is for scale 0.02 h/Mpc, from \url{https://ui.adsabs.harvard.edu/abs/2018MNRAS.477.1604G/abstract}, and our figure 2 shows that it should be possible to make measurements using our method on scales of ~0.002 h/Mpc, which are ~10 times larger.
 

### 2020-02-20 paper/v2.tex
1

@@
 \newcommand{\sfiggg}[2]{
-\includegraphics[width=0.4\paperwidth]{../plots/#1}
+\includegraphics[width=0.8\paperwidth]{../plots/#1}
         }
@@
    \begin{figure}[thbp]
-    \sfigg{../plots/#1.pdf}{.8\paperwidth}
+    \sfiggg{../plots/#1.pdf}{.8\paperwidth}
     \caption{{\small #2}}
@@
 The information contained on large scales may provide information about issues ranging from the turnover in the power spectrum (and therefore the total matter density) to the accelerated universe to anomalies observed in the cosmic microwave background to primordial nongaussianity.
-Direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered.
+\peikai{In \cite{Karkare:2019delen}, a method of using delensing with intensity mapping has been proposed to directly measure large scale modes.} But generally speaking, direct measurements are difficult because of observational systematic effects, so indirect approaches have been considered.
+\peikai{As pointed out by \cite{Modi:2019hydr}, 21cm intensity mapping is one area where due to foregrounds, large-scale (line of sight) modes will be impossible to measure directly.}
+
 Small scale structure grows differently in the presence of an large-scale overdensity: it is as if the mean background density is larger than on average.
@@
 
-\noindent{\it Quadratic Estimator.}\label{sec2}
+\section{Quadratic Estimator}\label{sec2}
 We can now construct the quadratic estimator for long-wavelength modes starting from \ec{2pt} and summing over as many pairs as possible with weights that maximize the signal-to-noise.
@@
 In Fig.~\rf{SN}, we show the projected errors on the long-wavelength power spectrum using this quadratic estimator in a large survey.
-The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$.
+\peikai{The current largest scale published measurement of the three dimensional power spectrum is for scale $0.02 \, h \,\rm Mpc^{-1}$, from \cite{Gil-Marin:2018SDSS}.
+And our Fig.~\rf{SN} shows that it should be possible to make measurements using our method on scales of $0.002 \, h \,\rm Mpc^{-1}$, which are $\sim$10 times larger.} The upper limit of the $\vk_s$ integration in \ec{a} is set to be $0.22\,h\,\rm Mpc^{-1}$.
 We will see that this choice of the upper limit is reasonable for our current construction at $z=0$.
@@
 In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
+\peikai{Similarly to this construction, kSZ velocities \cite{Kosowsky:2009ksz} might also be a good tracer of large-scale modes.
+We can take the advantage of it's small scale information and potentially get a better constraint of large-scale modes.
+We will leave this part to future work.}
+
 The estimator works well on an N-Body simulation, so applying this estimator to survey data is \peikai{the logical} next step.
@@
 There is evidence of large scale anomalies, in the CMB, that could be confronted with maps of large scale structure obtained with this estimator.
-Primordial non-Gaussianity generated by inflation leaves an imprint on the largest scales.
+\peikai{One physical mechanism that has been proposed as a possible explanation for the deficit in the large-angle CMB temperature correlations is a suppression of primordial power on $\sim$ Gpc scales \cite{Hearin:2011anom}.
+It would be very useful to verify if this new physics is also present in other probes of large-scale structure.} Primordial non-Gaussianity generated by inflation leaves an imprint on the largest scales.
 There is even the possibility of cross-correlating the large-scale matter field with the CMB itself to extract information about the longest wavelength modes in the universe.
